---
title: "2026 ACC/AHA Lipid Guidelines Update"
subtitle: "An Analysis from NHANES"
format: 
  html:
    toc: true
    toc-expand: true
    toc-location: body
date: 09-09-2024
theme: lightly
author:
  - name: "Ahmed Sayed (asu.ahmed.sayed@gmail.com)"
    affiliations: "Rochester General Hospital, Rochester, New York, USA"
embed-resources: true
toc-title: Contents
page-layout: full
code-fold: true
editor: visual
editor_options: 
  chunk_output_type: console
---

# Setup

## Libraries

```{r}
#Load libs
packs <- c("data.table", "dplyr", 
           "stringr", "haven", "PooledCohort",
           "ggplot2", "scales",  "survey",
           "flextable", "ggsci", "ggthemes",
           "scales", "Hmisc", "legendry",
           "forcats", "rms"
           )
lapply(packs, require, character.only = TRUE)
options(survey.lonely.psu = "adjust")
```

## Self-made functions

### Analytic

```{r}
#Quantiles
qs <- function(variable) quantile(variable, seq(0, 1, 0.05), na.rm = T)

#Functions to create PE/CI
make_pe_ci_mil <- function(pe, lci, uci) {
  paste0(pe %>% tomil,
         " [", lci %>% tomil, " to ", uci %>% tomil, "]") %>% str_replace("\\[ ", "\\[")
}

make_pe_ci <- function(pe, lci, uci, round_n = 1) {
  paste0(pe %>% round(round_n) %>% format(nsmall = round_n),
         " [", lci %>% round(round_n) %>% format(nsmall = round_n), " to ", uci %>% round(round_n) %>% format(nsmall = round_n), "]") %>% str_replace("\\[ ", "\\[")
}

make_prop_pe_ci <- function(prop_pe, prop_lci, prop_uci) {
paste0( (100*prop_pe) %>% r1,
                                " [", (100*prop_lci) %>% r1, " to ", (100*prop_uci) %>% r1, "]") %>% str_replace("\\[ ", "\\[")
}

make_prop_pe_ci_pct <- function(prop_pe, prop_lci, prop_uci) {
  paste0( (100*prop_pe) %>% r1,
          "% [95%CI: ", (100*prop_lci) %>% r1, " to ", (100*prop_uci) %>% r1, "%]") %>%
    str_replace("\\[ ", "\\[")
  
}        


#Function to rename columns. Please note that this is a more general function not intended purely for this analysis and therefore contains other variables irrelevant to it.
nhanes_rename <- function(x) { x %>% rename(any_of(c(
  #Survey cycle and demographics
  "survey_cycle" = "SDDSRVYR",
  "age" = "RIDAGEYR",
  "sex" = "RIAGENDR",
  "race" = "RIDRETH3",
  #Medical conditions
  "htn" = "BPQ020",
  "dyslipid" = "BPQ080",
  "dm" = "DIQ010",
  "pre_dm" = "DIQ160",
  "chd" = "MCQ160C",
  "angina" = "MCQ160D",
  "mi" = "MCQ160E",
  "stroke" = "MCQ160F",
  "smoke_100" = "SMQ020",
  "smoke_now" = "SMQ040",
  "cancer" = "MCQ220",
  "dialysis" = "KIQ025",
  "failing_kidney" = "KIQ022",
  "hf" = "MCQ160B",
  #Medical recommendations
  "salt_adv_take" = "MCQ371C",
  "chol_meds_adv" = "BPQ090D",
  "chol_meds_take" = "BPQ100D",
  "htn_meds_adv" = "BPQ040A",
  "htn_meds_take" = "BPQ050A",
  "aspirin_adv" = "RXQ510",
  "aspirin_adv_take" = "RXQ515",
  "aspirin_indep" = "RXQ520",
  #Exam data
  "sbp_1" = "BPXOSY1",
  "sbp_2" = "BPXOSY2",
  "sbp_3" = "BPXOSY3",
  "sbp_1" = "BPXSY1",
  "sbp_2" = "BPXSY2",
  "sbp_3" = "BPXSY3",
  "dbp_1" = "BPXODI1",
  "dbp_2" = "BPXODI2",
  "dbp_3" = "BPXODI3",
  "dbp_1" = "BPXDI1",
  "dbp_2" = "BPXDI2",
  "dbp_3" = "BPXDI3",
  "bmi" = "BMXBMI",
  "waist" = "BMXWAIST",
  #Lab values
  "fasting_glucose" = "LBXGLU",
  "hba1c" = "LBXGH",
  "apo_b" = "LBXAPB",
  "ldl" = "LBDLDL",
  "ldl_mh" = "LBDLDLM",
  "ldl_nih" = "LBDLDLN",
  "tg" = "LBXTR",
  "hdl" = "LBDHDD",
  "tc" = "LBXTC",
  "creatinine" = "LBXSCR",
  "urine_creatinine" = "URXUCR",
  "urine_albumin" = "URXUMS",
  "platelets" = "LBXPLTSI",
  "hiv_combo_1516" = "LBXHIVC",
  "hiv_confirm_1516"= "LBXHNAT",
  "hiv_1114" = "LBDHI"
  
)))
}


#Import an nhanes file given an NHANES folder and file
import_nhanes <- function(nhanes_pair) {
          
          #State directory of files
          files <- dir(paste0(nhanes_dir, nhanes_pair[1])) %>%
            #select relevant data
            str_subset("(_I|_H|_G)\\.|P_")
          
          
          #Import files in a given subfolder (lapply is not needed here, but it is made to be more general in case you need more than 1 file a year)
          lapply(files,
                 function(file) {
                    
                    #Read the file
                    data <- read_xpt(file = paste0(nhanes_dir, 
                                                   nhanes_pair[1], "/", 
                                                   file)
                                     )
                    #Rename columns
                    data <- nhanes_rename(data)
                    
                    #If meds, start command to join medications together
                    if(nhanes_pair[2] == "meds") {
                      
                      #Join medications together
                      if("RXDDRUG" %in% colnames(data)) {
                        data <- data %>%
                          group_by(SEQN) %>%
                          summarise(drug_names = paste(RXDDRUG, collapse = "; ")
                                    )
                        
                      } else if("RXD240B" %in% colnames(data)) {
                        
                        data <- data %>%
                          group_by(SEQN) %>%
                          summarise(drug_names = paste(RXD240B, collapse = "; "),
                                    )
                      }
                    }
                    
                    #Return the object
                    data
                   
                 }
                    
          ) %>%
            #Use rbindlist in case you are importing several years at once
            rbindlist(fill = T) -> data
          
          
}

#Convert 1/0 binaries
convert_10 <- function(x) ifelse(x == 1, "yes", "no") %>% factor


#Convert variables coded as 1279 in NHANES to Yes/No
convert_1279 <- function(variable, yes_ind = "Yes", no_ind = "No") {
  fcase(variable == 1, yes_ind,
        variable == 2, no_ind)
}

#Convert variables coded as 123479 in NHANES to Yes/No (this is for aspirin use)
convert_123479 <- function(variable, yes_ind = "Yes", no_ind = "No") {
  fcase(variable %in% c(1, 3), yes_ind,
        variable %in% c(2, 4), no_ind)
}



#Convert race for PCE (White and Black only; everyone is assigned to White if they're not Black)
convert_race_pce <-  function(variable) {
  fcase(variable %in% c(1, 2, 3, 6, 7), "white",
        variable == 4, "black"
        )
}

#Convert race
convert_race_complete <-  function(variable) {
  fcase(variable %in% c(1, 2), "Hispanic",
        variable == 3, "Non-Hispanic White",
        variable == 4, "Non-Hispanic Black",
        variable == 6, "Non-Hispanic Asian",
        variable == 7, "Other (including multiracial)"
        )
}

#Function to indicate if drug was taken
find_drug <- function(drugs_column, drug_string, yes_ind = "Yes", no_ind = "No") {
  fifelse(str_detect(drugs_column, drug_string), yes_ind, no_ind)
}

#Function to indicate if indication is present
find_ind <- function(inds_column, ind_string, yes_ind = "Yes", no_ind = "No") {
  fifelse(str_detect(inds_column, ind_string), yes_ind, no_ind)
}


#Create a function to get survey means and CIs
svymean_df <- function(design, variables) {
  
  #Get chosen variables in the form of "or"
  variables[2] %>%
    #Convert to character
    paste0 %>%
    #Replace + with or
    str_replace_all("\\+", "\\|") %>%
    #Squish together
    str_replace_all(" \\| ", "\\|") -> chosen_vars
  
  #Get the part of svymean's name that corresponds to the variable name
  svymean(design = design, variables, na.rm = T) %>%
    names %>%
    str_extract(chosen_vars) -> chosen_vars
  
  
  #Produce data.table containing the information on totals
  data.table(
    #Variable
    var = chosen_vars,
    #Variable level
    #Total
    pe = svymean(design = design, variables, na.rm = T) %>%
      data.frame %>%
      {.$mean},
    #LCI
    lci = svymean(design = design, variables, na.rm = T) %>% confint %>% data.frame %>% {.$X2.5..},
    #UCI
    uci = svymean(design = design, variables, na.rm = T) %>% confint %>% data.frame %>% {.$X97.5..}
  ) -> mean_df
  
  
  #Add PE/CI col
  mean_df[, pe_ci := make_pe_ci(pe, lci, uci)]
  
  #Return
  print(mean_df)
  
}

 # design = subset(sdata, llt == "no" & old_1 == "no" & age < 40)
 # variables = ~ old_2b
# design = subset(sdata, eval(four_group_filters[[3]]) & llt == "yes" & race == "Non-Hispanic Black"); variables = ~ ldl_cat
# design = subset(sdata,llt == "yes" & race == "Non-Hispanic White"); variables = ~ ldl_cat
#Create a function to neatly get survey totals/proportions and confidence intervals
svytotal_df <- function(design, variables) {
  
  
  
  #Get chosen variables in the form of "or"
  variables[2] %>%
    #Convert to character
    paste0 %>%
    #Replace + with or
    str_replace_all("\\+", "\\|") %>%
    #Squish together
    str_replace_all(" \\| ", "\\|") -> chosen_vars
  
  if(nrow(design$variables) == 0) df <- data.table(
  value = "yes",
  pe = 0,
  lci = 0,
  uci = 0,
  prop_pe = 0,
  prop_lci = 0,
  prop_uci = 0,
  pe_ci = 0,
  prop_pe_ci = 0,
  prop_pe_ci_pct = 0
) else {
  
  #Get the part of svytotal's name that corresponds to the variable name
  svytotal(design = design, variables, na.rm = T) %>%
    names %>%
    str_extract(chosen_vars) -> chosen_vars
  
  #Get the part of svytotal's name that corresponds to the variable value
  svytotal(design = design, variables, na.rm = T) %>%
    names %>%
    str_remove_all(chosen_vars) -> chosen_vars_levels
  
  #Produce data.table containing the information on totals
  data.table(
    #Variable
    var = chosen_vars,
    #Variable level
    value = chosen_vars_levels,
    #Total
    pe = svytotal(design = design, variables, na.rm = T) %>%
      data.frame %>%
      {.$total},
    #LCI
    lci = svytotal(design = design, variables, na.rm = T) %>% confint %>% data.frame %>% {.$X2.5..},
    #UCI
    uci = svytotal(design = design, variables, na.rm = T) %>% confint %>% data.frame %>% {.$X97.5..}
  ) -> total_df
  
  
  
  lapply(chosen_vars_levels,
         function(level) {
           form <- bquote(~ .(variables[[2]]) == .(level))
           #Get proportion
           svyciprop(design = design, 
          formula = form, na.rm = T
          ) %>% {data.table(
               prop_pe = .[1],
               prop_lci = attr(., "ci") %>% .["2.5%"],
               prop_uci = attr(., "ci") %>% .["97.5%"]
             )}
         }
  ) %>%
    rbindlist -> props_df
  
  #Bind
  df <- cbind(total_df, props_df)
  
  #Make pe/ci columns
  df[, pe_ci := make_pe_ci_mil(pe, lci, uci) %>% str_squish]
  df[, prop_pe_ci :=  make_prop_pe_ci(prop_pe, prop_lci, prop_uci) %>% str_squish]
  df[, prop_pe_ci_pct :=  make_prop_pe_ci_pct(prop_pe, prop_lci, prop_uci) %>% str_squish]

}
  
  
  #Return
  df
  
}

#Function to bootstrap differences in eligibility
boot_diff <- function(survey_object = sdata_rep, call_var) {
withReplicates(
  design = survey_object,
  return.replicates = T,
  theta = call_var
) -> rep_result

  #Collect
  data.table(prop_pe = rep_result$theta[1],
             prop_uci = rep_result$replicates %>% quantile(c(0.975)),
             prop_lci = rep_result$replicates %>% quantile(c(0.025))
             ) -> rep_result_df
  
  #Calculate absolutes
  rep_result_df[, pe := prop_pe * sum(survey_object$variables$weight)]
  rep_result_df[, lci := prop_lci * sum(survey_object$variables$weight)]
  rep_result_df[, uci := prop_uci * sum(survey_object$variables$weight)]
  
  #Return
  print(rep_result_df)
}

#Difference (without bootstrap, using a simplifying normality assumption)
#Test
# survey_object = sdata %>% subset(llt == "no")
# cond1 = expr(new_2a == "yes" & new_1 == "no")
# cond2 = expr(old_2b == "yes" & old_1 == "no")

diff_fn <- function(survey_object, cond1, cond2) {
svymean(design = survey_object,
        ~ 
          I(eval(cond1)) +
          I(eval(cond2)),
        na.rm = T) -> svymean_object

svycontrast(stat = svymean_object,
            list(diff_new_old = 
              c(
                `I(eval(cond1))TRUE` = 1,
                `I(eval(cond2))TRUE` = -1
              )
            )
            ) -> svycontrast_object

data.table(prop_pe = svycontrast_object,
           prop_lci = svycontrast_object %>% confint %>% {.[, 1]},
           prop_uci = svycontrast_object %>% confint %>% {.[, 2]}) -> result_df

#Calculate absolutes
result_df[, pe := prop_pe * sum(survey_object$variables$weight)]
result_df[, lci := prop_lci * sum(survey_object$variables$weight)]
result_df[, uci := prop_uci * sum(survey_object$variables$weight)]

#Return
result_df
}


```

### Aesthetic

```{r}

#Create PE (CI) column
pe_ci <- function(pe = pe, lci = lci, uci = uci, rounding = 2) {
  paste0(
    pe  %>% round(rounding) %>% format(nsmall = rounding), " (", 
    lci %>% round(rounding) %>% format(nsmall = rounding), " to ",
    uci  %>% round(rounding) %>% format(nsmall = rounding),
    ")"
  )
}


#Functions to format p
p <- function(p) {
  ifelse(p < 0.001, "<0.001", ifelse(round(p, 2) == 0.05 | round(p, 2) == 0, round(p, 3) %>% format(nsmall = 3), round(p, 3) %>% format(nsmall = 3))) %>% as.character
}

#Loop over numeric variables, sex, and binary (Yes/no) variables and summarize
sum_var <- function(dataset, variable) {
  #Numeric vars 
  if(variable %in% numeric_variables) {
    dataset[, 
      paste0(median(get(variable), na.rm = T) %>% round(1) %>% format(nsmall = 1),
             " (", 
             iqr(get(variable)), ")"
      )
    ]
  } 
  
  #Sex
  else if(variable %>% str_detect("sex|gender")) {
    paste0(dataset[get(variable) %in% c("female", "Female", "Women", "women"), .N] %>% scales::comma(),
           " (", (100*dataset[get(variable) %in% c("female", "Female", "Women", "women"), .N]/dataset[, .N]) %>% r1, "%)")
  }
  
  #Binary vars
  else if(variable %in% binary_variables) {
    paste0(dataset[get(variable) %in% c("Yes", "yes"), .N] %>% scales::comma(),
           " (", (100*dataset[get(variable) %in% c("Yes", "yes"), .N]/dataset[, .N]) %>% r1, "%)")
  }
}


#Get IQRs
iqr <- function(x, rounding = 1) {
  paste0(
    quantile(x, 0.25, na.rm = T) %>% round(rounding) %>% format(nsmall = rounding),
    " to ",
    quantile(x, 0.75, na.rm = T) %>% round(rounding) %>% format(nsmall = rounding)
  )
  
}

#Round to 1 decimal and include zero if needed
r1 <- function(x) {
  x %>% round(1) %>% format(nsmall = 1)
}

#Round to 2 decimals and include zero if needed
r2 <- function(x) {
  x %>% round(2) %>% format(nsmall = 2)
}

#Convert to million
tomil <- function(x) {
  format(round(x / 1e6, 1), nsmall = 1, trim = T)
}

#Perform some aesthetic modifications for flextables
flextable_aes <- function(table, table_title) {
  
  #Table font
  table <- flextable::font(table, fontname = "Times New Roman", part = "all")
  
  #Align everything centrally
  table <- flextable::align(table, align = "center", part = "all")
  
  #Table heading
  table <- flextable::set_caption(table, caption = table_title)
  
  #Align footer to the left
  table <- flextable::align(table, align = "left", part = "footer")
  
  
  #Set Table width
  table <- flextable::width(table, width = 1.5, unit = "in")
  
  #Bold
  table <- flextable::bold(table, part = "header")
  
  #Borders
  table <- table %>% border_inner %>% border_outer
  
  #Print
  table
}


```

## Import

```{r}

#The lefthand side is the name of the folder in which the respective NHANES data files should be deposited. The lefthand side is the name that will be used for the data.frame in R
folders_dfs <- list(
  c("Demographics", "demo"),
  c("LDL_TG_Measure", "ldl_tg_measure"),
  c("TC_measure", "tc_measure"),
  c("HDL_Measure", "hdl_measure"),
  c("Glycohemoglobin", "hba1c"),
  c("Fasting_Glucose", "fasting_glucose"),
  c("BMI", "bmi"),
  c("BP_Measure", "bp_measure"),
  c("BP_Chol", "bp_chol"),
  c("Diabetes", "dm_df"),
  c("Smoke", "smoke_df"),
  c("Urine albumin and creatinine", "urine_alb_cr"),
  c("Medical Conditions", "med_conds"),
  c("Biochem Profile", "biochem"),
  c("Meds", "meds"),
  c("Kidney", "kidney"),
  c("ApoB", "apo_b"),
  c("HIV", "hiv")
)

#Get NHANES directory (INSERT YOUR OWN DIRECTORY HERE)
nhanes_dir <- "C:/Ahmed's Stuff/ResearchStuff/NHANES_Data/"

#Lapply to import NHANES data for a given set of variables
lapply(folders_dfs, function(folder) import_nhanes(folder)) -> data

#Use Reduce to successively merge elements of the data list
Reduce(function(x, y) merge(x, y, all = T, by = "SEQN"), data) -> data

##TABLE 1 FUNCTION
table1_create <- function(dataset, variables, table1_title, 
                          strata_var = NULL, 
                          p_values = FALSE,
                          p_values_col_ind = 5,
                          table_width = 3,
                          numeric_variables, binary_variables
) {
  
  #Store variable names
  var_names <- names(variables)
  
  
  #Get overall CCs using the sum_var function
  lapply(var_names, function(variable) sum_var(dataset, variable)) -> overall_values
  
  #Create strata CCs using the same but with an additional layer of looping for strata levels
  if(!is.null(strata_var)) {
    
    #Strata levels  
    strata_levels <- dataset[, get(strata_var) %>% factor %>% levels]
    
    #Apply over levels of strata of interest
    lapply(1:length(strata_levels),
           function(i)
           {
             stratum <- strata_levels[[i]]
             #CCs of level 1
             lapply(var_names, function(variable) sum_var(dataset = dataset[get(strata_var) == stratum], variable)) %>%
               unlist
           }
    ) -> strata_values
    
    
  }
  
  
  #Create data.table containing the relevant variables
  data.table(
    variable_names = variables %>% unlist,
    variable_values = overall_values %>% unlist
  ) -> table1_df
  
  #Create new columns with the corresponding values for each strata
  if(!is.null(strata_var)) {
    for(i in 1:length(strata_values)) {
      table1_df[, paste0("level_", i) := strata_values[[i]]]
      setnames(table1_df, old = paste0("level_", i), new = strata_levels[i])
    }
  }
  
  #Get p-values if necessary
  if(p_values) {
    #Loop over variables to get test statistics
    lapply(var_names, 
           function(var_name) test_var(dataset, variable = var_name, strata_var)) %>% unlist -> pvals
    table1_df[, p_values := pvals]
  }
  
  #Rename and create a flextable
  table1_df %>%
    rename(any_of(c(
      "Variables" = "variable_names",
      "Overall" = "variable_values",
      "P-values*" = "p_values"
    ))) %>%
    flextable %>% 
    flextable_aes(table1_title) %>%
    bold(j = 1) %>%
    width(width = table_width) -> table_flex
  
  #Add P-value if relevant
  if(p_values) {
    table_flex <- footnote(table_flex, 
             ref_symbols = footnote_symbol(1), 
             j = p_values_col_ind,
             value = as_paragraph("P-values were obtained from Wilcoxon test for continuous variables or from a Chi-square test for categorical variables."))
  }
  
  #Produce table
  table_flex
}
```

## Modify LDL to MH

```{r}
#Create empty x column
data[, mh_factor := NA]


#Non-HDL
data[, non_hdl := tc - hdl]

#Convert stata code to R (to create the script necessary to create the Martin Hopkins factor)
mh_factor_script <- readLines("statacode.do") %>%
  str_replace("if", "data$mh_factor[") %>% #Replace if
  {.[. != ""]} %>% #Remove empty lines
  {.[c(-1, -length(.) )]} %>% #Remove first and last line
  paste0("]") %>% #Put bracket at end of each line
  str_replace_all("nonhdl", "data$non_hdl") %>% #Replace nonhdl by appropriate symbol
  str_replace_all("tg", "data$tg") %>% #Replace tg by appropriate symbol
  str_remove_all("replace|factor=") %>% #Remove replace and factor= 
  paste("<-", word(., 2))  %>% #Relocate conversion factor where appropriate
  str_remove(word(., 2)) %>% #Remove the number at the beginning
  str_trim %>% #Remove unnecessary space at beginning
  str_replace("\\[ ", "\\[") #Remove unnecccessary space after "["

#Run script (which is now written in a format usable in R)
eval(parse(text = mh_factor_script))

#Get MH estimate
data[, ldl := tc - (hdl + (tg/mh_factor))]
data[ldl < 0, ldl := NA]

```

## Clean & Prep

```{r}

#Convert variables coded as 1, 2, 7, or 9
columns_1279 <- c("pre_dm", "dm", "htn", "smoke_100",
                  "chd", "mi", "stroke", "angina", 
                  "cancer", "htn_meds_adv", "htn_meds_take",
                  "failing_kidney", "dialysis", "hf", "hiv_combo_1516", "hiv_confirm_1516",  "hiv_1114"
                  )
data[, (columns_1279) := lapply(.SD, convert_1279, "yes", "no"), 
     .SDcols = columns_1279]
data[failing_kidney == "no", dialysis := "no"]
#Convert hypertension meds to no if appropriate 
data[, htn_meds_take := fifelse(htn == "no" | htn_meds_adv == "no", "no", htn_meds_take)]



#Convert sex
data[, sex := fcase(
    sex == 1, "male",
    sex == 2, "female"
)]

#Convert hiv
data[, hiv := fcase(
  (hiv_combo_1516 == "yes" & is.na(hiv_confirm_1516)) | hiv_confirm_1516 == "yes" | hiv_1114 == "yes", "yes",
  hiv_1114 == "no" | hiv_confirm_1516 == "no" | (hiv_combo_1516 == "yes" & hiv_confirm_1516 == "no"), "no"
)]

#Build a string for statins
statin_string <- c("(?i)LOVASTATIN|PRAVASTATIN|FLUVASTATIN|ROSUVASTATIN|PITAVASTATIN|ATORVASTATIN|SIMVASTATIN|CERIVASTATIN")
pcks9_string <- c("(?i)EVOLOCUMAB|ALIROCUMAB")
eze_string <- c("(?i)EZETIMIBE")

#Indicate drug use
data[, statin := find_drug(drug_names, statin_string, "yes", "no")]
data[, pcsk9 := find_drug(drug_names, pcks9_string, "yes", "no")]
data[, ezetimibe := find_drug(drug_names, eze_string, "yes", "no")]
data[, llt := fifelse(statin == "yes" | pcsk9 == "yes" | ezetimibe == "yes", "yes", "no")]



#Convert race
data[, race_pce := convert_race_pce(race)]
data[, race := convert_race_complete(race)]
data[, black := fifelse(race == "Non-Hispanic Black", "yes", "no")]
data[, hispanic := fifelse(race == "Hispanic", "yes", "no")]
data[, white := fifelse(race == "Non-Hispanic White", "yes", "no")]
data[, asian := fifelse(race == "Non-Hispanic Asian", "yes", "no")]
data[, other := fifelse(race == "Other (including multiracial)", "yes", "no")]

#Convert current smoking habits
data[, smoke_now := fcase(
  smoke_now == 1, "yes",
  smoke_now == 2, "yes",
  smoke_now == 3, "no",
  smoke_100 == "no", "no"
)]

#Create obesity
data[, obesity := fifelse(bmi >= 30, "yes", "no")]

#Calcualte avg systolic and diastolic BP
#Create BP variables that take the mean of any number of measurements
library(kit)
data[, sbp := pmean(sbp_1, sbp_2, sbp_3, na.rm = T)]
data[, dbp := pmean(dbp_1, dbp_2, dbp_3, na.rm = T)]


#Define DM drug use use
insulin_string <- c("INSULIN|LISPRO|ASPART|GLULISINE|NPH|GLARGINE|DETEMIR|DEGLUDEC")
ddp4_string <- c("SITAGLIPTIN|LINAGLIPTIN|ALOGLIPTIN|SAXAGLIPTIN")
tzds_string <- c("REPAGLINIDE|NATEGLINIDE")
sulfonylureas_string <- c("GLIPIZIDE|GLIMEPIRIDE|GLYBURIDE|GLICLAZIDE|TOLBUTAMIDE|CARBUTAMIDE|TOLAZAMIDE|CHLORPROPAMIDE")
meglitinides_string <- c("PIOGLITAZONE|ROSIGLITAZONE")
insulin_string <- c("INSULIN|LISPRO|ASPART|GLULISINE|NPH|GLARGINE|DETEMIR|DEGLUDEC")
amylin_string <- c("PRAMLINTIDE")

data[, insulin := find_drug(drug_names, insulin_string, "Yes", "No")]
data[, ddp4 := find_drug(drug_names, ddp4_string, "Yes", "No")]
data[, tzds := find_drug(drug_names, tzds_string, "Yes", "No")]
data[, sulfonylureas := find_drug(drug_names, sulfonylureas_string, "Yes", "No")]
data[, meglitinides := find_drug(drug_names, meglitinides_string, "Yes", "No")]
data[, insulin := find_drug(drug_names, insulin_string, "Yes", "No")]
data[, amylin := find_drug(drug_names, amylin_string, "Yes", "No")]
data[, dm_drug := fifelse(str_detect(paste0(insulin, ddp4, tzds, sulfonylureas, meglitinides, insulin, amylin), "Yes"), "Yes", "No")]


#Define DM
data[, dm := fcase(
  hba1c >= 6.5 | fasting_glucose >= 126 | dm == "yes" | dm_drug == "Yes", "yes",
  dm == "no" | hba1c < 6.5 | fasting_glucose < 126, "no"
  )]

#Calculate sex-specific constants for eGFR estimation
data[, alpha := fifelse(sex == "male", -0.302, -0.241)]
data[, k := fifelse(sex == "male", 0.9, 0.7)]
data[, constant := fifelse(sex == "male", 1, 1.012)]

#Calculate eGFR
data[, egfr :=
    142 *
    (pmin(creatinine/k, 1)^alpha) *
    (pmax(creatinine/k, 1)^-1.2) *
    (0.9938^age) *
    constant
    ]

#Create age cats for inverse probability matching
data[, age_cats := cut(age, seq(0, 90, 10), include.lowest = T)]

#Create albumin/creatinine ratio
data[, uacr := urine_albumin/(10*urine_creatinine/1000)]

#Estimate pre-treatment LDL/non-HDL
data[, ldl_multiplier := 1]
data[, non_hdl_multiplier := 1]
##For statins
#LDL (Per Marcusa 2020, Assuming a 45.2% reduction)
data[statin == "yes", ldl_multiplier := ldl_multiplier / (1-0.452)]
#Non-HDL (Per Mora 2012, assuming a 40.3% reduction)
data[statin == "yes", non_hdl_multiplier := non_hdl_multiplier / (1-0.403)]

##For PCSK9
#LDL (Per Marcusa 2020, Assuming a 62.3% reduction)
data[pcsk9 == "yes", ldl_multiplier := ldl_multiplier / (1-0.623)]
#Non-HDL (Per Supplementary Figure S3 in the FOURIER trial, assuming a 51.6% reduction)
data[pcsk9 == "yes", non_hdl_multiplier := non_hdl_multiplier / (1-0.516)]

##For Ezetimibe
#LDL (Per Marcusa 2020, Assuming a 25.8% reduction)
data[ezetimibe == "yes", ldl_multiplier := ldl_multiplier / (1-0.258)]
#Non-HDL (per Table S1 in the IMPROVE-IT trial, assuming a 19.9% reduction)
data[ezetimibe == "yes", non_hdl_multiplier := non_hdl_multiplier / (1-0.199)]


#Estimate pre-treatment cholesterol
data[, pre_ttt_ldl := ldl * ldl_multiplier]
data[, pre_ttt_non_ldl := non_hdl * non_hdl_multiplier]

```

## Calculate risk

```{r}

#Create capped versions of variables
data[, tc_cap := fcase(
  tc < 130, 130,
  tc > 320, 320,
  rep(TRUE, .N), tc
)]
data[, sbp_cap := fcase(
  sbp < 90, 90,
  sbp > 200, 200,
  rep(TRUE, .N), sbp
)]

data[, hdl_cap_prevent := fcase(
  hdl < 20, 20,
  hdl > 100, 100,
  rep(TRUE, .N), hdl
)]

data[, bmi_cap_prevent := fcase(
  bmi < 18.5, 18.5,
  bmi > 40, 40,
  rep(TRUE, .N), bmi
)]

data[, egfr_cap_prevent := fcase(
  egfr < 15, 15,
  egfr > 140, 140,
  rep(TRUE, .N), egfr
)]

data[, eligible := fifelse(
  age >= 30 & age <= 79, 1, 0
)]
#Calculate 10-year risk using PREVENT
data[eligible == 1, prevent_10yr := predict_10yr_ascvd_risk(
  age_years = age,
  sex = sex,
  bp_sys_mmhg = sbp_cap,
  bmi = bmi_cap_prevent,
  diabetes = dm,
  bp_meds = htn_meds_take,
  chol_total_mgdl = tc_cap,
  chol_hdl_mgdl = hdl_cap_prevent,
  statin_meds = statin,
  smoke_current = smoke_now,
  egfr = egfr_cap_prevent,
  equation = "Khan_2023"
)]

#Calculate 10-year risk using PREVENT
data[eligible == 1, prevent_30yr := predict_30yr_ascvd_risk(
  age_years = age,
  sex = sex,
  bp_sys_mmhg = sbp_cap,
  bmi = bmi_cap_prevent,
  diabetes = dm,
  bp_meds = htn_meds_take,
  chol_total_mgdl = tc_cap,
  chol_hdl_mgdl = hdl_cap_prevent,
  statin_meds = statin,
  smoke_current = smoke_now,
  egfr = egfr_cap_prevent,
  equation = "Khan_2023"
)]


data[, statin_num := fifelse(statin == "yes", 1, 0)]
data[, dm_num := fifelse(dm == "yes", 1, 0)]
data[, smoke_num := fifelse(smoke_now == "yes", 1, 0)]
data[, htn_meds_num := fifelse(htn_meds_take == "yes", 1, 0)]


#Calculate 10-year risk using more expansive PREVENT
# data[eligible == 1, prevent_10yr_more := predict_10yr_ascvd_risk(
#   age_years = age,
#   sex = sex,
#   bp_sys_mmhg = sbp_cap,
#   bmi = bmi_cap_prevent,
#   diabetes = dm,
#   hba1c = hba1c,
#   acr = uacr,
#   bp_meds = htn_meds_take,
#   chol_total_mgdl = tc_cap,
#   chol_hdl_mgdl = hdl_cap_prevent,
#   statin_meds = statin,
#   smoke_current = smoke_now,
#   egfr = egfr_cap_prevent,
#   sdi = NULL,
#   equation = "Khan_2023",
#   prevent_type = "base"
# )]

#Calculate 10-year risk using PCE
data[age >= 40 & age <= 75, pce_10yr := predict_10yr_ascvd_risk(
  age_years = age,
  race = race_pce,
  sex = sex,
  bp_sys_mmhg = sbp_cap,
  diabetes = dm,
  bp_meds = htn_meds_take,
  chol_total_mgdl = tc_cap,
  chol_hdl_mgdl = hdl_cap_prevent,
  smoke_current = smoke_now,
  equation = "Goff_2013"
)]

data[, sdi := NA]

#Calculate 10-year risk using the full PREVENT equation
data[age >= 30, prevent_10yr_uacr := predict_10yr_ascvd_risk(
  age_years = age,
  sex = sex,
  bp_sys_mmhg = sbp_cap,
  bmi = bmi_cap_prevent,
  diabetes = dm,
  bp_meds = htn_meds_take,
  chol_total_mgdl = tc_cap,
  chol_hdl_mgdl = hdl_cap_prevent,
  statin_meds = statin,
  smoke_current = smoke_now,
  egfr = egfr_cap_prevent,
  hba1c = hba1c,
  acr = uacr,
  sdi = sdi,
  equation = "Khan_2023",
  prevent_type = "acr"
)]

data[age >= 30, prevent_10yr_a1c := predict_10yr_ascvd_risk(
  age_years = age,
  sex = sex,
  bp_sys_mmhg = sbp_cap,
  bmi = bmi_cap_prevent,
  diabetes = dm,
  bp_meds = htn_meds_take,
  chol_total_mgdl = tc_cap,
  chol_hdl_mgdl = hdl_cap_prevent,
  statin_meds = statin,
  smoke_current = smoke_now,
  egfr = egfr_cap_prevent,
  hba1c = hba1c,
  acr = uacr,
  sdi = sdi,
  equation = "Khan_2023",
  prevent_type = "hba1c"
)]

#Calculate 10-year risk using the full PREVENT equation
data[age >= 30, prevent_10yr_uacr_a1c := predict_10yr_ascvd_risk(
  age_years = age,
  sex = sex,
  bp_sys_mmhg = sbp_cap,
  bmi = bmi_cap_prevent,
  diabetes = dm,
  bp_meds = htn_meds_take,
  chol_total_mgdl = tc_cap,
  chol_hdl_mgdl = hdl_cap_prevent,
  statin_meds = statin,
  smoke_current = smoke_now,
  egfr = egfr_cap_prevent,
  hba1c = hba1c,
  acr = uacr,
  sdi = sdi,
  equation = "Khan_2023",
  prevent_type = "full"
)]

#Define CVD
data[, ascvd := fifelse(mi == "yes" | stroke == "yes" | chd == "yes" | angina == "yes", 1, 0) %>% convert_10]
#Define CKD
data[, ckd := fifelse(uacr >= 30 | egfr <= 60, 1, 0) %>% convert_10]

#MetS (per Table 1 in https://www.ahajournals.org/doi/10.1161/cir.0000000000001184)
data[, met_syndrome := fifelse(
  rowSums(cbind(
    tg >= 150,
    sbp >= 130 | dbp >= 80 | htn_meds_take == "yes",
    hdl < 40 & sex == "male",
    hdl < 50 & sex == "female",
    waist > 102 & sex == "male",
    waist > 88 & sex == "female",
    fasting_glucose >= 100
  ), na.rm = TRUE) >= 3,
  1,
  0
)]

#2018 Risk factors (per Table 6 in the 2018 guidelines)
data[, rf_enhancers_2018 := fifelse(rowSums(cbind(ldl %between% c(160, 189.999),
                            non_hdl %between% c(190, 219),
                          egfr %between% c(15, 59),
                               apo_b >= 130,
                            met_syndrome == 1, na.rm = T)) >= 1,
                          1, 0
                          )]

#CKM definition (per Table 1 in https://www.ahajournals.org/doi/10.1161/cir.0000000000001184)
data[, ckm := fifelse(rowSums(cbind(ckd == 1 | met_syndrome == 1 | sbp >= 130 | dbp >= 80 | dm == "yes" | tg >= 135, na.rm = T)) >= 1, 1, 0)]

#RFs in 2026 (per Table 13 in 2026 guidelines)
data[, rf_enhancers_2026 := fifelse(rowSums(cbind(ldl %between% c(160, 189.999), 
                                            (non_hdl %between% c(190, 219)),
                                               apo_b >= 120,
                                               tg >= 150,
                                            ckd == "yes",
                                            tg >= 135,
                                            ckm == 1 ),
                                            na.rm = T) >= 1,
                                    1, 0)]
#Minus LDL/non-HDL criteria for those with LDL>190
data[, rf_enhancers_2026_minus_lipids := fifelse(rowSums(cbind(
                                               apo_b >= 120,
                                               tg >= 150,
                                            ckd == "yes",
                                            tg >= 135,
                                            ckm == 1 ),
                                            na.rm = T) >= 1,
                                    1, 0)]

#Minus LDL/non-HDL criteria for DM
data[, rf_enhancers_2026_minus_ckm := fifelse(rowSums(cbind(ldl %between% c(160, 189.999), 
                                            (non_hdl %between% c(190, 219)),
                                               apo_b >= 120,
                                               tg >= 150,
                                            ckd == "yes",
                                            tg >= 135),
                                            na.rm = T) >= 1,
                                    1, 0)]

#N Lacking 10-year risk estimates
lacking_risk_n <- data[(is.na(pce_10yr) | is.na(prevent_10yr)), .N]

```

## Assign CoR

```{r}


##1 by BOTH guidelines
# LDL >190
data[, v_high_ldl_eligible_2026 := fifelse(pre_ttt_ldl >= 190, 1, 0)]
data[, v_high_ldl_eligible_2018 := fifelse(pre_ttt_ldl >= 190 & age %between% c(20, 75), 1, 0)]

#DM with age 40-75
data[, dm_eligible := fifelse(dm == "yes" & age %between% c(40, 75), 1, 0)]
#ASCVD
data[, ascvd_eligible := fifelse(ascvd == "yes", 1, 0)]


###By 2026 ONLY
##1
##PREVENT-based 
#Base
data[, prevent_high_intermediate_eligible := fifelse(prevent_10yr %between% c(0.05, 0.1), 1, 0)]
data[, prevent_high_eligible := fifelse(prevent_10yr >= 0.1, 1, 0)]
#UACR
data[, prevent_uacr_high_intermediate_eligible := fifelse(prevent_10yr_uacr %between% c(0.05, 0.1), 1, 0)]
data[, prevent_uacr_high_eligible := fifelse(prevent_10yr_uacr >= 0.1, 1, 0)]
#A1c
data[, prevent_a1c_high_intermediate_eligible := fifelse(prevent_10yr_a1c %between% c(0.05, 0.1), 1, 0)]
data[, prevent_a1c_high_eligible := fifelse(prevent_10yr_a1c >= 0.1, 1, 0)]
#UACR and A1c
data[, prevent_uacr_a1c_high_intermediate_eligible := fifelse(prevent_10yr_uacr_a1c %between% c(0.05, 0.1), 1, 0)]
data[, prevent_uacr_a1c_high_eligible := fifelse(prevent_10yr_uacr_a1c >= 0.1, 1, 0)]


#CKD stage III (without dialysis)
data[, ckd_eligible := fifelse(egfr < 60 & dialysis == "no" & ldl %between% c(70, 189), 1, 0)]

##2A
data[, prevent_low_intermediate_eligible := fifelse(prevent_10yr %between% c(0.03, 0.0499999), 1, 0)]
data[age < 30 | age == 80, prevent_low_intermediate_eligible := 0] #0 if outside PREVENT-usable age-range

data[, prevent_low_eligible := fifelse(prevent_10yr <= 0.3 &
                                         (ldl %between% c(160, 189) | prevent_30yr >= 0.1),
                                       1, 0)]
data[!age %between% c(30, 59), prevent_low_eligible := 0] #0 if outside eligible age range
data[, new_2a_ldl30 := prevent_low_eligible %>% convert_10]
#data[, new_2a := pmax(prevent_low_eligible, prevent_low_intermediate_eligible, na.rm = T) %>% convert_10]
data[, new_2a := fifelse(prevent_low_intermediate_eligible == 1 | new_2a_ldl30 == "yes", 1, 0) %>% convert_10]


###2018 ONLY
##2B
data[, pce_intermediate_eligible := fifelse(pce_10yr %between% c(0.05, 0.07499999), 1, 0)]
data[age < 40 | age > 75, pce_intermediate_eligible := 0]
##1
data[, pce_high_eligible := fifelse(pce_10yr > 0.075, 1, 0)]


#Recs by class
data[, new_1 := pmax(v_high_ldl_eligible_2026,
                      dm_eligible,
                      ascvd_eligible,
                      ckd_eligible,
                      prevent_high_eligible,
                      prevent_high_intermediate_eligible,
                      na.rm = T) %>% convert_10]
data[, new_2a_not_1 := fifelse(new_2a == "yes" & new_1 == "no", "yes", "no") %>% factor]


data[, new_12a := pmax(v_high_ldl_eligible_2026,
                      dm_eligible,
                      ascvd_eligible,
                      ckd_eligible,
                      prevent_high_eligible,
                      prevent_high_intermediate_eligible,
                      prevent_low_intermediate_eligible,
                      prevent_low_eligible,
                      na.rm = T) %>% convert_10]

data[, new_1_uacr := pmax(v_high_ldl_eligible_2026,
                      dm_eligible,
                      ascvd_eligible,
                      ckd_eligible,
                      prevent_uacr_high_eligible,
                      prevent_uacr_high_intermediate_eligible,
                      na.rm = T) %>% convert_10]

data[, new_1_a1c := pmax(v_high_ldl_eligible_2026,
                      dm_eligible,
                      ascvd_eligible,
                      ckd_eligible,
                      prevent_a1c_high_eligible,
                      prevent_a1c_high_intermediate_eligible,
                      na.rm = T) %>% convert_10]

data[, new_1_uacr_a1c := pmax(v_high_ldl_eligible_2026,
                      dm_eligible,
                      ascvd_eligible,
                      ckd_eligible,
                      prevent_uacr_a1c_high_eligible,
                      prevent_uacr_a1c_high_intermediate_eligible,
                      na.rm = T) %>% convert_10]


data[, new_1_reason := fcase(ascvd_eligible == 1, "ASCVD",
                             v_high_ldl_eligible_2026 == 1, "LDL-C greater than 190 mg/dL",
                             dm_eligible == 1, "Diabetes mellitus (aged 40 to 75 years)",
                             ckd_eligible == 1, "Stage III CKD not on dialysis",
                             prevent_high_eligible == 1 | prevent_high_intermediate_eligible == 1, "PREVENT-based ASCVD 10-year risk of 5% or more")]



#Old
data[, old_1 := pmax(v_high_ldl_eligible_2018,
                      dm_eligible,
                      ascvd_eligible,
                      pce_high_eligible,
                      na.rm = T) %>% convert_10]

data[, old_12b := pmax(v_high_ldl_eligible_2018,
                      dm_eligible,
                      ascvd_eligible,
                      pce_high_eligible,
                      pce_intermediate_eligible,
                      na.rm = T) %>% convert_10]

data[, old_2b := pce_intermediate_eligible %>% convert_10]
data[, old_2b_not_1 := fifelse(old_2b == "yes" & old_1 == "no", "yes", "no") %>% factor]

data[, old_1_reason := fcase(ascvd_eligible == 1, "ASCVD",
                             v_high_ldl_eligible_2018 == 1, "LDL-C greater than 190 mg/dL",
                             dm_eligible == 1, "Diabetes mellitus (aged 40 to 75 years)",
                             pce_high_eligible == 1, "PCE-based ASCVD 10-year risk of 7.5% or more")]


#Discordance
data[, discordant_type := fcase(
  new_1 == "no" & old_1 == "no", "Concordant (no class I recommendation to treat)",
  new_1 == "yes" & old_1 == "yes", "Concordant (class I recommendation to treat)",
  old_1 == "no" & new_1 == "yes"  , "Discordant (new class I recommendation to treat)",
    old_1 == "yes" & new_1 == "no"  , "Discordant (no longer has class I recommendation to treat)"
) %>% factor]

data[, discordant_type := fct_relevel(discordant_type,
                                      c("Concordant (no class I recommendation to treat)",
                                        "Concordant (class I recommendation to treat)",
                                        "Discordant (new class I recommendation to treat)",
                                        "Discordant (no longer has class I recommendation to treat)"
                                        )
                                      )]

data[, discordant_2_type := fcase(
  new_2a_not_1 == "no" & old_2b_not_1 == "no", "Concordant (no class II recommendation to treat)",
  new_2a_not_1 == "yes" & old_2b_not_1 == "yes", "Concordant (class II recommendation to treat)",
  old_2b_not_1 == "no" & new_2a_not_1 == "yes"  , "Discordant (new class II recommendation to treat)",
  old_2b_not_1 == "yes" & new_2a_not_1 == "no"  , "Discordant (no longer has class II recommendation to treat)"
) %>% factor]

data[, discordant_12_type := fcase(
  new_12a == "no" & old_12b == "no", "Concordant (no class I/II recommendation to treat)",
  new_12a == "yes" & old_12b == "yes", "Concordant (class I/II recommendation to treat)",
  old_12b == "no" & new_12a == "yes"  , "Discordant (new class I/II recommendation to treat)",
  old_12b == "yes" & new_12a == "no"  , "Discordant (no longer has class I/II recommendation to treat)"
) %>% factor]

data[, discordant_12_type := fct_relevel(discordant_12_type,
                                      c("Concordant (no class I/II recommendation to treat)",
                                        "Concordant (class I/II recommendation to treat)",
                                        "Discordant (new class I/II recommendation to treat)",
                                        "Discordant (no longer has class I/II recommendation to treat)"
                                        )
                                      )]


data[, new_2a_ldl30 := fifelse(
  prevent_10yr < 0.03 & age %between% c(30, 59) &
  (ldl %between% c(160, 189) | (prevent_30yr >= 0.1) ) &
    ascvd == "no" & (dm == "no" | age < 40 | age > 75) & egfr >= 60
    ,
  "yes", "no")]


#Eligible for CACS measurement if uncertainty re: LLT decision
cacs_eligible_exp <- expr(prevent_10yr %between% c(0.03, 0.1) &
                        ((age >= 40 & sex == "male") | (age >= 45 & sex == "female")) &
       llt == "no" & egfr >= 60 & dm == "no" & ldl < 190 & ascvd == "no")
data[, cacs_eligible := fifelse(eval(cacs_eligible_exp), "yes", "no") %>% factor]

```


## Goals

```{r}

#MODIFY TO ADD ZETIA
#Define v high risk ASCVD
data[, vh_risk_ascvd := fifelse(ascvd == "yes" & 
                                  ((mi == "yes" & stroke == "yes") |
                                  age >= 65 | smoke_now == "yes" | dm == "yes" | hf == "yes" | htn == "yes" | 
                                    (ldl > 100 & statin == "yes" & ezetimibe == "yes")),
                                "yes", "no"
                                  )]

#Define goals
data[, goal_100_130 := fifelse(new_1 == "yes" & 
                                 (prevent_10yr < 0.1 |
                                    pre_ttt_ldl >= 190 |
                                    dm == "yes" 
                                    ),
                               1, 0
                                 )]

data[, goal_70_100 := fifelse(new_1 == "yes" & 
                                 (prevent_10yr >= 0.1 |
                                    (pre_ttt_ldl >= 190 & rf_enhancers_2026_minus_lipids == 1) |
                                    (dm == "yes" & rf_enhancers_2026_minus_ckm == 1) |
                                    (ascvd == "yes" & vh_risk_ascvd == "no")
                                 ),
                               1, 0
)]

data[, goal_55_85 := fifelse(new_1 == "yes" & 
                                (( (pre_ttt_ldl >= 190 | tg >= 150 | vh_risk_ascvd == "yes")  & ascvd == "yes")
                                ),
                              1, 0
)]

#Give goal
data[, goal := fcase(
  goal_55_85 == 1, "LDL-C/non-HDL-C targets of <55/<85 mg/dL",
  goal_70_100 == 1, "LDL-C/non-HDL-C targets of <70/<100 mg/dL",
  goal_100_130 == 1, "LDL-C/non-HDL-C targets of <100/<130 mg/dL"
) %>% factor]


#ApoB goals
data[, apo_b_goal := fcase(
  (dm == 1 | prevent_10yr %between% c(0.05, 0.0999)) & goal == "LDL-C/non-HDL-C targets of <100/<130 mg/dL", "ApoB target of <90 mg/dL",
  (dm == 1 | prevent_10yr >= 0.1) & goal == "LDL-C/non-HDL-C targets of <70/<100 mg/dL", "ApoB target of <70 mg/dL",
  vh_risk_ascvd == "yes", "ApoB target of <55 mg/dL"
)]


#LDL cats
data[, ldl_cat := fcase(
  ldl < 55, "LDL-C <55 mg/dL",
  ldl %between% c(55, 69.999999), "LDL-C 55-69 mg/dL",
  ldl %between% c(70, 99.99999999), "LDL-C 70-99 mg/dL",
  ldl >= 100, "LDL-C of 100 mg/dL or greater"
) %>% factor]

#Goal needs based on LDL and non-HDL
data[, goal_need := fcase(
  goal_55_85 == 1 & (ldl >= 55 | non_hdl >= 85), "Requires intensification to meet LDL-C/non-HDL-C targets of <55/<85 mg/dL",
  goal_70_100 == 1 & (ldl >= 70 | non_hdl >= 100), "Requires intensification to meet LDL-C/non-HDL-C targets of <70/<100 mg/dL",
  goal_100_130 == 1 & (ldl >= 100 | non_hdl >= 130), "Requires intensification to meet LDL-C/non-HDL-C targets of <100/<130 mg/dL",
  (goal_55_85 == 1 & (ldl < 55 | non_hdl < 85)) | (goal_70_100 == 1 & (ldl < 70 | non_hdl < 100)) | (goal_100_130 == 1 & (ldl < 100 | non_hdl < 130)),
  "At goal"
  ) %>% factor]


#Goal needs based on LDL only
data[, goal_need_ldl := fcase(
  goal_55_85 == 1 & (ldl >= 55), "Requires intensification to meet LDL-C target of <55 mg/dL",
  goal_70_100 == 1 & (ldl >= 70), "Requires intensification to meet LDL-C target of <70 mg/dL",
  goal_100_130 == 1 & (ldl >= 100), "Requires intensification to meet LDL-C target of <100 mg/dL",
  (goal_55_85 == 1 & (ldl < 55)) | (goal_70_100 == 1 & (ldl < 70)) | (goal_100_130 == 1 & (ldl < 100)),
  "At goal"
  ) %>% factor]

#Goal needs based on non-HDL-only
data[, goal_need_non_hdl := fcase(
  goal_55_85 == 1 & (non_hdl >= 85), "Requires intensification to meet non-HDL-C target of <85 mg/dL",
  goal_70_100 == 1 & (non_hdl >= 100), "Requires intensification to meet non-HDL-C target of <100 mg/dL",
  goal_100_130 == 1 & (non_hdl >= 130), "Requires intensification to meet non-HDL-C target of <130 mg/dL",
  (goal_55_85 == 1 & (non_hdl < 85)) | (goal_70_100 == 1 & (non_hdl < 100)) | (goal_100_130 == 1 & (non_hdl < 130)),
  "At goal"
  ) %>% factor]

#Meets LDL but not non-HDL
data[, goal_need_non_hdl_not_ldl := fcase(
  goal_55_85 == 1 & ldl < 55 & non_hdl >= 85, "Requires intensification to meet non-HDL-C target of <85 mg/dL",
  goal_70_100 == 1 & ldl < 70 & (non_hdl >= 100), "Requires intensification to meet non-HDL-C target of <100 mg/dL",
  goal_100_130 == 1 & ldl < 100 & (non_hdl >= 130), "Requires intensification to meet non-HDL-C target of <130 mg/dL",
  default = "Concordant"
)]

#Meets non-HDL but not LDL-C
data[, goal_need_ldl_not_non_hdl := kit::nif(
  goal_55_85 == 1 & ldl >= 55 & non_hdl < 85, "Requires intensification to meet LDL-C target of <55 mg/dL",
  goal_70_100 == 1 & ldl >= 70 & (non_hdl < 100), "Requires intensification to meet LDL-C target of <70 mg/dL",
  goal_100_130 == 1 & ldl >= 100 & (non_hdl < 130), "Requires intensification to meet LDL-C target of <100 mg/dL",
  default = "Concordant"
)]


#Goal needs according to LDL and non-HDL (3 cats)
data[, goal_need_ldl_non_hdl := fcase(
  goal_need_ldl != "At goal", "Does not meet LDL-C goal",
  goal_need_ldl == "At goal" & goal_need_non_hdl != "At goal", "Meets LDL-C but not non-HDL-C goal",
  goal_need_ldl == "At goal" & goal_need_non_hdl == "At goal", "Meets both LDL-C and non-HDL-C goal"
) %>% factor]

#ApoB goal attainment
data[, goal_need_apo_b := fcase(
  apo_b_goal == "ApoB target of <90 mg/dL" & apo_b >= 90, "Requires intensifcation to meet apoB target of <90 mg/dL",
  apo_b_goal == "ApoB target of <70 mg/dL" & apo_b >= 70, "Requires intensifcation to meet apoB target of <70 mg/dL",
  apo_b_goal == "ApoB target of <55 mg/dL" & apo_b >= 55, "Requires intensifcation to meet apoB target of <55 mg/dL",
  default = "At goal"
  
)]

#Goal needs according to LDL and apoB
data[, goal_need_ldl_apo_b := fcase(
  goal_need_ldl != "At goal", "Does not meet LDL-C goal",
  goal_need_ldl == "At goal" & goal_need_apo_b != "At goal", "Meets LDL-C but not apoB goal",
  goal_need_ldl == "At goal" & goal_need_apo_b == "At goal", "Meets both LDL-C and apoB goal"
) %>% factor]


data[, goal_need_3 := fcase(
  goal_need_ldl != "At goal", "Does not meet LDL-C goal",
  goal_need_ldl == "At goal" & goal_need_non_hdl != "At goal", "Meets LDL-C but not non-HDL-C goal",
  goal_need_ldl == "At goal" & goal_need_non_hdl == "At goal" & goal_need_apo_b != "At goal", "Meets LDL-C and non-HDL-C but not apoB goal",
  goal_need_ldl == "At goal" & goal_need_non_hdl == "At goal" & goal_need_apo_b == "At goal", "Meets LDL-C, non-HDL-C, and apoB goals"
  
  
)]

```

## Impute mean values for eGFR

```{r}
#Create backup copy
data[, egfr_o := copy(egfr)]

#Impute
data[(WTSAF2YR > 0 | WTSAFPRP.x > 0), 
     egfr := wtd.mean(x = egfr_o, w = c(WTSAF2YR, WTSAFPRP.x) %>% na.omit,
                           na.rm = T)]


```

## Create new propensity weights

```{r}
#Adjust survey weights to reflect proportion of data from each cycle (these weights are not yet adjusted for item nonresponse)
data[survey_cycle != 66, pre_adj_weight := WTSAF2YR * 2/data[, 1.2 + uniqueN(survey_cycle)*2]] 
data[survey_cycle == 66, pre_adj_weight := WTSAFPRP.x * 3.2/data[, 1.2 + uniqueN(survey_cycle)*2]] 
# setnames(data, "WTMEC2YR", "pre_adj_weight")
# data[, pre_adj_weight := pre_adj_weight/uniqueN(survey_cycle)]

#Propensity model
glm(data = data[age >= 20 & pre_adj_weight > 0], 
    weight = pre_adj_weight/mean(pre_adj_weight),
    family = "binomial", 
    !is.na(new_1) & (!is.na(new_2a_not_1)) & !is.na(old_1) & (!is.na(old_2b_not_1)) ~ rms::rcs(age, 6) * sex * race) -> mprop

#Invert predicted probability of response
data[age >= 20 & pre_adj_weight > 0, inv_probs := 1/predict(mprop, .SD, type = "response")]


#Create new adjusted weights
data[!is.na(new_1) & (!is.na(new_2a_not_1)) & !is.na(old_1) & (!is.na(old_2b_not_1)), weight := inv_probs * pre_adj_weight]
data[, weight := weight * (data[age >= 20 & pre_adj_weight > 0, 
                                sum(pre_adj_weight)/sum(weight, na.rm = T)])] #Renormalize to equalize to target population

#Check that the resultant weights add up
all.equal(data[age >= 20 & !is.na(new_1) & !is.na(old_1) & !is.na(new_2a_not_1) & !is.na(old_2b_not_1),
               sum(weight, na.rm = T)],
          round(data[age >= 20, sum(pre_adj_weight, na.rm = T)]))
data[is.na(weight), weight := 0]
```

## Create weights for LDL

```{r}
#Weights for ppl with ldl
data[survey_cycle != 66, pre_adj_weight_ldl := WTSAF2YR * 2/data[, 1.2 + uniqueN(survey_cycle)*2]] 
data[survey_cycle == 66, pre_adj_weight_ldl := WTSAFPRP.x * 3.2/data[, 1.2 + uniqueN(survey_cycle)*2]] 

#Propensity model for ppl with ldl
glm(data = data[age >= 20 & pre_adj_weight > 0 & new_1 == "yes" & llt == "yes"], 
    weight = pre_adj_weight/mean(pre_adj_weight),
    family = "binomial", 
    !is.na(goal_need_3) ~ rcs(age, 6) * sex * race) -> mprop_ldl

#Invert predicted probability of response for ppl with ldl
data[age >= 20 & pre_adj_weight_ldl > 0, 
     inv_probs_ldl := 1/predict(mprop_ldl, .SD, type = "response")]

#Create new adjusted weights for ppl with ldl
data[!is.na(goal_need_3) & new_1 == "yes" & llt == "yes", weight_ldl := inv_probs_ldl * pre_adj_weight_ldl]

data[, weight_ldl := weight_ldl * (data[age >= 20 & new_1 == "yes" & llt == "yes",
                                          sum(weight)/sum(data$weight_ldl, na.rm = T)])] #Renormalize to equalize to target population

#Set weights to 0 if applicable
data[is.na(weight_ldl), weight_ldl := 0]


```

## Create weights for Subset of ppl with HIV

```{r}
#Weights for ppl with HIV
data[survey_cycle != 66, pre_adj_weight_hiv := WTSAF2YR * 2/data[survey_cycle != 66, uniqueN(survey_cycle)*2]] 

#Propensity model for ppl with HIV
glm(data = data[age >= 20 & pre_adj_weight_hiv > 0], 
    weight = pre_adj_weight_hiv/mean(pre_adj_weight_hiv),
    family = "binomial", 
    !is.na(new_1) & (!is.na(new_2a_not_1)) & !is.na(old_1) & (!is.na(old_2b_not_1)) ~ rcs(age, 6) * sex * race) -> mprop_hiv

#Invert predicted probability of response for ppl with HIV
data[age >= 20 & pre_adj_weight_hiv > 0, 
     inv_probs_hiv := 1/predict(mprop_hiv, .SD, type = "response")]

#Create new adjusted weights for ppl with HIV
data[!is.na(new_1) & !is.na(old_1), weight_hiv := inv_probs_hiv * pre_adj_weight_hiv]
data[, weight_hiv := weight_hiv * (data[age >= 20,
                                          sum(weight)/sum(data$weight_hiv, na.rm = T)])] #Renormalize to equalize to target population

#Set weights to 0 if applicable
data[is.na(weight_hiv), weight_hiv := 0]



```

## Create weights for treatment goal (apoB; only until 2016)

## Create weights for treatment goal (apoB; only until 2016)

```{r}
#Weights for ppl with apoB
data[survey_cycle != 66, pre_adj_weight_apob := WTSAF2YR * 2/data[survey_cycle != 66, uniqueN(survey_cycle)*2]] 

#Propensity model for ppl with apoB
glm(data = data[age >= 20 & pre_adj_weight_apob > 0 & new_1 == "yes" & llt == "yes"], 
    weight = pre_adj_weight_apob/mean(pre_adj_weight_apob),
    family = "binomial", 
    !is.na(goal_need_3) ~ rcs(age, 6) * sex * race) -> mprop_apob

#Invert predicted probability of response for ppl with apoB
data[age >= 20 & pre_adj_weight_apob > 0, 
     inv_probs_apob := 1/predict(mprop_apob, .SD, type = "response")]

#Create new adjusted weights for ppl with apoB
data[!is.na(goal_need_3) & new_1 == "yes" & llt == "yes", weight_apob := inv_probs_apob * pre_adj_weight_apob]

data[, weight_apob := weight_apob * (data[age >= 20 & new_1 == "yes" & llt == "yes",
                                          sum(weight)/sum(data$weight_apob, na.rm = T)])] #Renormalize to equalize to target population

#Set weights to 0 if applicable
data[is.na(weight_apob), weight_apob := 0]



```


## Convert to a survey object

```{r}


#Make survey object out of x
sdata <- svydesign(data = data,
                ids = data$SDMVPSU,
                strata = data$SDMVSTRA,
                weights = data$weight,
                nest = TRUE)

# bp_exclusion <- expr(is.na(sbp) | is.na(dbp))
# age_exclusion <- expr(age < 20)
# 
# missing_age_n <- data[eval(age_exclusion), .N]
# missing_bp_n <- data[!eval(age_exclusion)][eval(bp_exclusion) & weight > 0, .N]
# missing_rec_exclusion <- data[!eval(age_exclusion)][!eval(bp_exclusion) & weight > 0][(is.na(new_1) | is.na(old_1) | is.na(new_1_mod)) & weight > 0, .N]

#Subset
subset(sdata, 
       subset = 
         #Limit to 20+
         age >= 20  &
         #Exclude if unavailable class I recommendation
       !is.na(new_1) & !is.na(old_1) & (!is.na(new_2a_not_1)) & (!is.na(old_2b_not_1)) & weight > 0
         ) -> sdata


#Make survey object out of x for HIV
sdata_hiv <- svydesign(data = data,
                ids = data$SDMVPSU,
                strata = data$SDMVSTRA,
                weights = data$weight_hiv,
                nest = TRUE)


```

## HIV numbers

```{r}
#Overall
svytotal_df(sdata_hiv %>% subset(age %between% c(40, 75)), variables = ~ hiv) -> hiv_df
#By sex
svytotal_df(sdata_hiv %>% subset(age %between% c(40, 75) & hiv == "yes"), variables = ~ sex) -> hiv_sex_df
#How many were eligible based on old guidelines?
svytotal_df(sdata_hiv %>% subset(age %between% c(40, 75) & hiv == "yes"), variables = ~ old_1) -> hiv_old_df
#Modify the formating of the pe-ci column since they're all <1m
hiv_sex_df[, pe_ci_form := paste0(pe %>% comma, " [95%CI: ", lci %>% comma, " to ", uci %>% comma, "]")]
hiv_df[, pe_ci_form := paste0(pe %>% comma, " [95%CI: ", lci %>% comma, " to ", uci %>% comma, "]")]
hiv_old_df[, pe_ci_form := paste0(pe %>% comma, " [95%CI: ", lci %>% comma, " to ", uci %>% comma, "]")]
rm(sdata_hiv)

```


# Analyze

##Baseline CCs table

```{r}

abbs_line <- "ACC: American College of Cardiology; AHA: American Heart Association; ASCVD: Atherosclerotic Cardiovascular disease; CKD: Chronic kidney disease; NH: Non-Hispanic"
explanation_line <- "Chronic kidney disease was defined by an eGFR <60 mL/min/1.73 m² or a urine albumin-creatinine ratio ≥30mg/g. Obesity was defined by a body mass index ≥25mg/kg². Diabetes was defined by an HbA1c ≥6.5%, fasting glucose ≥126mg/dL, a self-reported history of diabetes, or use of medications specific to diabetes. ASCVD was defined by a self-reported history of myocardial infarction, coronary heart disease, angina, or stroke"


#Wtd-media-iqr function
wtd_median_iqr <- function(var, wt, rounding = 0) {
  paste0(round(wtd.quantile(var, weights = wt, na.rm = T)[3], rounding) %>% format(nsmall = rounding),
         " (", round(wtd.quantile(var, weights = wt, na.rm = T)[2], rounding) %>% format(nsmall = rounding),
         " to ",
         round(wtd.quantile(var, weights = wt, na.rm = T)[4], rounding) %>% format(nsmall = rounding),
         ")")
}

library(Hmisc)
list(c("Number of survey respondents (N)", sdata$variables[, .N %>% comma]),
     c("Number of US adults (N, in millions)", sdata$variables[, sum(weight) %>% tomil]),
     c("Age (years)", sdata$variables[, wtd_median_iqr(age, weight)]),
     c("Proportion of women (%)", sdata$variables[, sum(weight[sex == "female"]/sum(weight))] %>% {r1(.*100)}),
     c("Race/Ethnicity (%)", ""),
     c("   Non-Hispanic White", sdata$variables[, sum(weight[race == "Non-Hispanic White"]/sum(weight))] %>% {r1(.*100)}),
     c("   Non-Hispanic Black", sdata$variables[, sum(weight[race == "Non-Hispanic Black"]/sum(weight))] %>% {r1(.*100)}),
     c("   Hispanic", sdata$variables[, sum(weight[race == "Hispanic"]/sum(weight))] %>% {r1(.*100)}),
     c("   Non-Hispanic Asian", sdata$variables[, sum(weight[race == "Hispanic"]/sum(weight))] %>% {r1(.*100)}),
     c("   Other (including multiracial)", sdata$variables[, sum(weight[race == "Other (including multiracial)"]/sum(weight))] %>% {r1(.*100)}),
     c("Body mass index (kg/m2)", sdata$variables[!is.na(bmi), wtd_median_iqr(bmi, weight, 1)]),
     c("Systolic Blood pressure (mmHg)", sdata$variables[!is.na(sbp), wtd_median_iqr(sbp, weight, 0)]),
     c("Diastolic Blood pressure (mmHg)", sdata$variables[!is.na(dbp), wtd_median_iqr(dbp, weight, 0)]),
     c("HbA1c (%)", sdata$variables[!is.na(hba1c), wtd_median_iqr(hba1c, weight, 1)]),
     c("Low-density lipoprotein cholesterol (mg/dL)", sdata$variables[!is.na(ldl), wtd_median_iqr(ldl, weight, 0)]),
     c("Total cholesterol (mg/dL)", sdata$variables[!is.na(tc), wtd_median_iqr(tc, weight, 0)]),
     c("High-density lipoprotein cholesterol (mg/dL)", sdata$variables[!is.na(hdl), wtd_median_iqr(hdl, weight, 0)]),
     c("Non-High-density lipoprotein cholesterol (mg/dL)", sdata$variables[!is.na(hdl) & !is.na(tc), wtd_median_iqr(tc - hdl, weight, 0)]),
     c("Triglycerides (mg/dL)", sdata$variables[!is.na(ldl), wtd_median_iqr(tg, weight, 0)]),
     c("Cardiovascular risk factors (%)", ""),
     c("   Obesity", sdata$variables[!is.na(bmi), sum(weight[bmi >= 30]/sum(weight))] %>% {r1(.*100)}),
     c("   Diabetes", sdata$variables[!is.na(dm), sum(weight[dm == "yes"]/sum(weight))] %>% {r1(.*100)}),
     c("   Hypertension", sdata$variables[!is.na(htn), sum(weight[htn == "yes"]/sum(weight))] %>% {r1(.*100)}),
     c("   CKD", sdata$variables[!is.na(ckd), sum(weight[ckd == "yes"]/sum(weight))] %>% {r1(.*100)}),
     c("   eGFR ≤59 ml/min/1.73m^2^", sdata$variables[!is.na(egfr), sum(weight[egfr <= 59]/sum(weight))] %>% {r1(.*100)}),
     c("   UACR ≥30 mg/g", sdata$variables[!is.na(uacr), sum(weight[uacr >= 30]/sum(weight))] %>% {r1(.*100)}),
     c("   LDL-C ≥190 mg/dL", sdata$variables[!is.na(ckd), sum(weight[ckd == "yes"]/sum(weight))] %>% {r1(.*100)}),
     c("   Smoking", sdata$variables[!is.na(smoke_now), sum(weight[smoke_now == "yes"]/sum(weight))] %>% {r1(.*100)})
) %>%
  {tibble(
    `Variable` = lapply(., "[[", 1) %>% unlist,
    `Value` = lapply(., "[[", 2) %>% unlist
  )} -> baseline_table

flextable(baseline_table) %>%
  border_inner %>%
  border_outer %>%
  merge_h %>%
  bold(i = 1, part = "header") %>%
  bold(j = 1) %>%
  flextable::font(fontname = "Times New Roman") %>%
  add_footer_row(values = as_paragraph("LDL-C: Low-density lipoprotein cholesterol; eGFR: Estimated glomerular filtration rate; UACR: Urine albumin-to-creatinine ratio"), colwidths = 2) %>%
  add_footer_row(values = as_paragraph("Data for binary variables are displayed as percentages. Data for continuous variables are shown as medians and interquartile ranges."), colwidths = 2) %>%
  add_footer_row(values = as_paragraph(explanation_line), colwidths = 2) %>%
  flextable_aes(paste0("Supplementary Table 5. Baseline characteristics of survey respondents (N = ", sdata$variables[, .N] %>% comma, ")")) %>%
  
  width(width = 3.5) -> baseline_table_t
  save_as_docx(baseline_table_t, path = "Tables/Supplementary Table 5.docx")

```

##Missing data characterization

```{r}
#Tabulate missing data %
list(
  c("Age", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(age)]/sum(weight)))]
  ),
  c("Sex", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(sex)]/sum(weight)))]
  ),
  c("Systolic blood pressure measurement", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(sbp)]/sum(weight)))]
  ),
  c("Diastolic blood pressure measurement", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(dbp)]/sum(weight)))]
  ),
  c("Body mass index", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(bmi)]/sum(weight)))]
  ),
  c("Diabetes", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(dm)]/sum(weight)))]
  ),
  c("Smoking", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(smoke_now)]/sum(weight)))]
  ),
  c("ASCVD", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(ascvd)]/sum(weight)))]
  ),
  c("HbA1c", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(hba1c)]/sum(weight)))]
  ),
  c("Total cholesterol", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(tc)]/sum(weight)))]
  ),
  c("High-density lipoprotein cholesterol", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(hdl)]/sum(weight)))]
  ),
  c("Creatinine**", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(creatinine)]/sum(weight)))]
  ),
  c("Urine albumin-creatinine ratio", 
    data[age >= 20, 
         r1(100*sum(weight[is.na(uacr)]/sum(weight)))]
  ),
  c("PREVENT ASCVD risk*", 
    data[age >= 20 & age %between% c(30, 79) & ascvd == "no" & ckd == "no" & egfr >= 60 & ldl < 190, 
         r1(100*sum(weight[is.na(prevent_10yr)]/sum(weight)))]
  ),
  c("PCE risk*", 
    data[age >= 20 & age %between% c(40, 75) & ascvd == "no" & ckd == "no" & ldl < 190, 
         r1(100*sum(weight[is.na(prevent_10yr)]/sum(weight)))]
  )
) %>%
  unlist %>%
  matrix(.,
         ncol = 2,
         byrow = T) %>%
  data.table -> missing_df
setnames(missing_df, new = c("Variable", "Weighted % missing"))

#Save as a word doc
missing_df %>% 
               flextable %>%
               border_inner %>%
               border_outer %>%
               merge_h %>%
               bold(i = 1, part = "header") %>%
               bold(j = 1) %>%
               set_caption(caption = as_paragraph("Supplementary Table 4. Weighted proportions of missing data among respondents.")) %>%
               flextable::font(fontname = "Times New Roman") %>%
               fontsize(size = 11) %>%
               add_footer_row(colwidths = 2, 
                              values = as_paragraph("*Estimated glomerular filtration rate in patients with a missing creatinine was imputed based on the weighted average of the study sample.\n**These proportions exclude participants who were not eligible for risk calculation because they were outside the validated range of either calculator and those with independent class I treatment recommendations.")) %>%
  width(width = c(4, 2.5)) -> missing_data_t
               
save_as_docx(missing_data_t, path = "Tables/Supplementary Table 4.docx")


```

## Function to get totals

```{r}

#Experiment
 # design = subset(sdata, llt == "no" & old_1 == "no")
 # var = ~ old_2b
 # include_ascvd = F
 # n_cats = 2



get_svytotals <- function(design = sdata, var, n_cats = 2, include_ascvd = TRUE) {

  lst <- list(
    #Overall
    " " = svytotal_df(design = design, 
                     variables = var) %>% mutate(group = "Overall"),
    
    #Age-stratified
    "Below 40" = svytotal_df(design = subset(design, age < 40), 
                            variables = var) %>% mutate(group = "Age (years)"),
    "40-64" = svytotal_df(design = subset(design, age %between% c(40, 64)), 
                         variables = var) %>% mutate(group = "Age (years)"),
    "65 or older" = svytotal_df(design = subset(design, age >= 65), 
                               variables = var) %>% mutate(group = "Age (years)"),
    
    #Sex-stratified
    "Female" = svytotal_df(design = subset(design, sex == "female"), 
                          variables = var) %>% mutate(group = "Sex"),
    "Male" = svytotal_df(design = subset(design, sex == "male"), 
                        variables = var) %>% mutate(group = "Sex"),
    
    #Race-stratified
    "NH Black" = svytotal_df(design = subset(design, race == "Non-Hispanic Black"), 
                            variables = var) %>% mutate(group = "Race and ethnicity"),
    "NH White" = svytotal_df(design = subset(design, race == "Non-Hispanic White"), 
                            variables = var) %>% mutate(group = "Race and ethnicity"),
    "NH Asian" = svytotal_df(design = subset(design, race == "Non-Hispanic Asian"), 
                            variables = var) %>% mutate(group = "Race and ethnicity"),
    "Hispanic" = svytotal_df(design = subset(design, race == "Hispanic"), 
                            variables = var) %>% mutate(group = "Race and ethnicity"),
    
    #Comorbidities
    "CKD" = svytotal_df(design = subset(design, ckd == "yes"), 
                       variables = var) %>% mutate(group = "Comorbidities"),
    "Obesity" = svytotal_df(design = subset(design, obesity == "yes"), 
                           variables = var) %>% mutate(group = "Comorbidities"),
    "Diabetes" = svytotal_df(design = subset(design, dm == "yes"), 
                            variables = var) %>% mutate(group = "Comorbidities"),
    "No CKD" = svytotal_df(design = subset(design, ckd == "no"), 
                          variables = var) %>% mutate(group = "Comorbidities"),
    "No Obesity" = svytotal_df(design = subset(design, obesity == "no"), 
                              variables = var) %>% mutate(group = "Comorbidities"),
    "No Diabetes" = svytotal_df(design = subset(design, dm == "no"), 
                               variables = var) %>% mutate(group = "Comorbidities")
  )

  # Conditionally add ASCVD
  if (include_ascvd) {
    lst[["ASCVD"]] <- svytotal_df(design = subset(design, ascvd == "yes"), 
                                 variables = var) %>% mutate(group = "Comorbidities")
  }

  #Store
  df <- data.table(
    rbindlist(lst) %>% select(-var),
    stratum = names(lst) %>% rep(each = n_cats)
  )
  
  #Print
  df
}



```

##Extract relevant subgroups

```{r}
subsets_calls_list <- list(
  quote(design),
  quote(subset(design, age < 40)),
  quote(subset(design, age %between% c(40, 64))),
  quote(subset(design, age >= 65)),
  quote(subset(design, sex == "female")),
  quote(subset(design, sex == "male")),
  quote(subset(design, race == "Non-Hispanic Black")),
  quote(subset(design, race == "Non-Hispanic White")),
  quote(subset(design, race == "Non-Hispanic Asian")),
  quote(subset(design, race == "Hispanic")),
  quote(subset(design, ckd == "yes")),
  quote(subset(design, ckd == "no")),
  quote(subset(design, obesity == "yes")),
  quote(subset(design, obesity == "no")),
  quote(subset(design, dm == "yes")),
  quote(subset(design, dm == "no")),
  quote(subset(design, ascvd == "yes"))
)


```

## Eligible for initiation

### Get numbers

#### Base (main)

#####1A

```{r}
#Eligibility under either guideline
get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_1) -> new_1_df
get_svytotals(design = subset(sdata, llt == "no"), var = ~ old_1) -> old_1_df


#Get differences in initiation eligibility
lapply(
  subsets_calls_list,
  function(subset_call) {
    diff_fn(survey_object = eval(subset_call, 
                                 envir = list(design = sdata %>%
            subset(llt == "no"))),
            cond1 = expr(new_1 == "yes"),
            cond2 = expr(old_1 == "yes")
          ) 
  }) -> abs_diff_init_df

abs_diff_init_df <- rbindlist(abs_diff_init_df)
abs_diff_init_df[, stratum := new_1_df$stratum %>% unique]
```

#####1A + 2

```{r}
#Eligibility under either guideline
get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_12a) -> new_12a_df
get_svytotals(design = subset(sdata, llt == "no"), var = ~ old_12b) -> old_12b_df


#Get differences in initiation eligibility
lapply(
  subsets_calls_list,
  function(subset_call) {
    diff_fn(survey_object = eval(subset_call, 
                                 envir = list(design = sdata %>%
            subset(llt == "no"))),
            cond1 = expr(new_12a == "yes"),
            cond2 = expr(old_12b == "yes")
          ) 
  }) -> abs_diff_init_df_12

abs_diff_init_df_12 <- rbindlist(abs_diff_init_df_12)
abs_diff_init_df_12[, stratum := new_1_df$stratum %>% unique]
```

#####2

```{r}
#Eligibility under either guideline
get_svytotals(design = subset(sdata, llt == "no"), include_ascvd = F, var = ~ new_2a_not_1) -> new_2a_df
get_svytotals(design = subset(sdata, llt == "no"), include_ascvd = F, var = ~ old_2b_not_1) -> old_2b_df

    diff_fn(survey_object = eval(subsets_calls_list[[1]], 
     envir = list(design = sdata %>%
                      subset(llt == "no"))),
            cond1 = expr(new_2a == "yes" & new_1 == "no"),
            cond2 = expr(old_2b == "yes" & old_1 == "no")
          ) -> o

#Get differences in initiation eligibility
lapply(
  subsets_calls_list,
  function(subset_call) {
    diff_fn(survey_object = eval(subset_call, 
                                 envir = list(design = sdata %>%
            subset(llt == "no"))),
            cond1 = expr(new_2a_not_1 == "yes"),
            cond2 = expr(old_2b_not_1 == "yes")
          ) 
  }) -> abs_diff_init_df_2

abs_diff_init_df_2 <- rbindlist(abs_diff_init_df_2)
abs_diff_init_df_2 <- abs_diff_init_df_2[-nrow(abs_diff_init_df_2)]
abs_diff_init_df_2[, stratum := new_2a_df$stratum %>% unique]
```


#### A1c and UACR

```{r}
get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_1_uacr_a1c) -> new_1_df_uacr_a1c

#Get differences in initiation eligibility
lapply(
  subsets_calls_list,
  function(subset_call) {
    diff_fn(survey_object = eval(subset_call, 
                                 envir = list(design = sdata %>%
            subset(llt == "no"))),
            cond1 = expr(new_1_uacr_a1c == "yes"),
            cond2 = expr(old_1 == "yes")
          ) 
  }) -> abs_diff_init_df_uacr_a1c

#Bind
abs_diff_init_df_uacr_a1c <- rbindlist(abs_diff_init_df_uacr_a1c)
abs_diff_init_df_uacr_a1c[, stratum := new_1_df$stratum %>% unique]
```

#### UACR

```{r}
get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_1_uacr) -> new_1_df_uacr

#Get differences in initiation eligibility
lapply(
  subsets_calls_list,
  function(subset_call) {
    diff_fn(survey_object = eval(subset_call, 
                                 envir = list(design = sdata %>%
            subset(llt == "no"))),
            cond1 = expr(new_1_uacr == "yes"),
            cond2 = expr(old_1 == "yes")
          ) 
  }) -> abs_diff_init_df_uacr

#Bind
abs_diff_init_df_uacr <- rbindlist(abs_diff_init_df_uacr)
abs_diff_init_df_uacr[, stratum := new_1_df$stratum %>% unique]

```

#### A1c

```{r}
get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_1_a1c) -> new_1_df_a1c



#Get differences in initiation eligibility
lapply(
  subsets_calls_list,
  function(subset_call) {
    diff_fn(survey_object = eval(subset_call, 
                                 envir = list(design = sdata %>%
            subset(llt == "no"))),
            cond1 = expr(new_1_a1c == "yes"),
            cond2 = expr(old_1 == "yes")
          ) 
  }) -> abs_diff_init_df_a1c

#Bind
abs_diff_init_df_a1c <- rbindlist(abs_diff_init_df_a1c)
abs_diff_init_df_a1c[, stratum := new_1_df$stratum %>% unique]


```


####Format and combine

```{r}
#Apply over dfs
lapply(list(old_1_df, 
            new_1_df, new_1_df_a1c, new_1_df_uacr, new_1_df_uacr_a1c,
            new_12a_df, new_2a_df, old_12b_df, old_2b_df,
            abs_diff_init_df, abs_diff_init_df_a1c, abs_diff_init_df_uacr, abs_diff_init_df_uacr_a1c,
            abs_diff_init_df_12, abs_diff_init_df_2),
       function(df)
       {
         df[, pe_ci := make_pe_ci_mil(pe, lci, uci) %>% str_squish]
         df[, prop_pe_ci :=  make_prop_pe_ci(prop_pe, prop_lci, prop_uci) %>% str_squish  %>% str_replace("\\[ ", "\\[")]
         df[, prop_pe_ci_pct :=  make_prop_pe_ci_pct(prop_pe, prop_lci, prop_uci) %>% str_squish %>% str_replace("\\[ ", "\\[")] 
       } 
       )

new_1_title <- "Eligible for treatment by the 2026 ACC/AHA Guideline"
old_1_title <- "Eligible for treatment by the 2018 ACC/AHA Guideline"

#Combine Base
rbind(new_1_df %>% mutate(type = new_1_title),
      old_1_df %>% mutate(type = old_1_title)
      ) -> eligibility_df
eligibility_df[, group := paste0(group, ".")]

#Combine A1c and UACR
rbind(new_1_df_uacr_a1c %>% mutate(type = new_1_title),
      old_1_df %>% mutate(type = old_1_title)
      ) -> eligibility_df_uacr_a1c
eligibility_df_uacr_a1c[, group := paste0(group, ".")]

#Combine UACR
rbind(new_1_df_uacr %>% mutate(type = new_1_title),
      old_1_df %>% mutate(type = old_1_title)
) -> eligibility_df_uacr

eligibility_df_uacr[, group := paste0(group, ".")]

#Combine A1c
rbind(new_1_df_a1c %>% mutate(type = new_1_title),
      old_1_df %>% mutate(type = old_1_title)
) -> eligibility_df_a1c
eligibility_df_a1c[, group := paste0(group, ".")]

#1/2
rbind(new_12a_df %>% mutate(type = new_1_title),
      old_12b_df %>% mutate(type = old_1_title)
) -> eligibility_df_12
eligibility_df_12[, group := paste0(group, ".")]

#2
rbind(new_2a_df %>% mutate(type = new_1_title),
      old_2b_df %>% mutate(type = old_1_title)
) -> eligibility_df_2
eligibility_df_2[, group := paste0(group, ".")]
```

### Plot I

#### Plot combined [not used]

```{r}
library(legendry)
eligibility_df[, stratum_group := interaction(stratum, group)]
eligibility_df[, stratum_group := factor(stratum_group,
                                         levels = eligibility_df$stratum_group %>%
                                           unique)]

#Plot
eligible_prop_fig_fn <- function(df) ggplot(data = df[value == "yes" & stratum != "ASCVD"],
           aes(y = prop_pe,
               ymin = prop_lci,
               ymax = prop_uci,
               x = stratum_group,
               fill = type,
               group = type
               )) +
      geom_col(position = position_dodge(width = 0.7),
               width = 0.7,
               color = "black", lwd = 1) +
      geom_errorbar(width = 0.5, lwd = 1,
                    position = position_dodge(width = 0.7)) +
      #Plot scales
        scale_x_discrete(name = NULL
                         ) +
      scale_y_continuous(name = "Eligible proportion (%)",
                         breaks = seq(0, 1, 0.05),
                         expand = c(0, 0),
                         labels = function(x) (x * 100) 
                         ) +
      scale_fill_stata(name = NULL) +
      guides(x = legendry::guide_axis_nested(key = key_range_auto("\\."))) +
      #Title
      ggtitle("Proportion of US adults eligible for initiating LDL-C-lowering therapy according to the 2018 and 2026 ACC/AHA guidelines",
              subtitle = "Bars represent estimated proportions and error bars represent 95% confidence intervals.") +
        theme_bw() +
        theme(title = element_text(size = 12, face = "bold"),
              plot.subtitle = element_text(face = "bold", size = 13, hjust = 0.0, color = "grey45"),
            text = element_text(size = 14, face = "bold"),
            axis.title.x = element_text(size = 18, face = "bold"),
            axis.title.y = element_text(size = 18, face = "bold"),
            axis.text = element_text(size = 16, face = "bold"),
            legend.position = "bottom",
            legend.key = element_rect(fill = "transparent"),
            legend.background = element_rect(fill = "transparent"),
            legend.text = element_text(size = 14, face = "bold"),
            legend.title = element_text(size = 17, face = "bold"),
            legend.key.width = unit(2, "cm")
            ) +
      coord_cartesian(
        ylim = c(0, 1)
      ) +
      guides(fill = guide_legend(nrow = 1))

eligible_prop_fig_fn(eligibility_df) -> eligible_prop_fig

#Predicted risks
ggsave(eligible_prop_fig,
       filename = "Figures/New vs Old eligible.pdf",
       dpi = 600,
       width = 16, height = 9
       )

```

#### Panel A [Age]

##### Calculate

```{r}

age_get_svytotals <- function(design = sdata, var, n_cats = 2) {
  list(
    "20-24" = svytotal_df(design = subset(design, age %between% c(20, 24)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "25-29" = svytotal_df(design = subset(design, age %between% c(25, 29)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "30-34" = svytotal_df(design = subset(design, age %between% c(30, 34)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "35-39" = svytotal_df(design = subset(design, age %between% c(35, 39)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "40-44" = svytotal_df(design = subset(design, age %between% c(40, 44)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "45-49" = svytotal_df(design = subset(design, age %between% c(45, 49)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "50-54" = svytotal_df(design = subset(design, age %between% c(50, 54)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "55-59" = svytotal_df(design = subset(design, age %between% c(55, 59)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "60-64" = svytotal_df(design = subset(design, age %between% c(60, 64)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "65-69" = svytotal_df(design = subset(design, age %between% c(65, 69)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "70-74" = svytotal_df(design = subset(design, age %between% c(70, 74)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "75 or older" = svytotal_df(design = subset(design, age %between% c(75, 80)), 
                          variables = var) %>% mutate(group = "Age (years)")
  ) %>% 
    {data.table(rbindlist(.) %>% select(-var),
                stratum = names(.) %>% rep(each = n_cats))} -> df
}


age_get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_1) -> age_new_1_df
age_get_svytotals(design = subset(sdata, llt == "no"), var = ~ old_1) -> age_old_1_df

rbind(age_old_1_df %>% mutate(type = "Eligible for treatment by the 2018 ACC/AHA Guideline"),
      age_new_1_df %>% mutate(type = "Eligible for treatment by the 2026 ACC/AHA Guideline")) %>%
  data.table -> age_df

```


##### Plot

```{r}

ggplot(data = age_df[value == "yes" & stratum %nin% c("20-24", "25-29")],
       aes(x = stratum, 
           y = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           fill = type)
) +
  #Geoms
  geom_col(width = 0.4, position = position_dodge(width = 0.5), lwd = 2) +
  geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
                position = position_dodge(width = 0.5)) +
  #Title
  ggtitle(label = "Proportion of untreated US adults with a class I recommendation for initiating LDL-C-lowering treatment, according to age") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Age (years)") +
  scale_y_continuous(name = "Percent of Population (%)",
                     labels = function(x) x * 100,
                     breaks = seq(0, 100, 5)/100,
                     sec.axis = dup_axis(name = NULL)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) +
  coord_cartesian(ylim = c(0, 1)) -> age_cat_fig

ggsave(age_cat_fig,
       filename = "Figures/Age categorical.pdf",
       dpi = 600, width = 16, height = 9)

```



#### Panel B [Age/sex]

##### Calculate


```{r}

age_sex_get_svytotals <- function(design = sdata, var, n_cats = 2) {
  list(
    "20-29" = svytotal_df(design = subset(design, age %between% c(20, 29)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "30-39" = svytotal_df(design = subset(design, age %between% c(30, 39)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "40-49" = svytotal_df(design = subset(design, age %between% c(40, 49)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "50-59" = svytotal_df(design = subset(design, age %between% c(50, 59)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "60-69" = svytotal_df(design = subset(design, age %between% c(60, 69)), 
                          variables = var) %>% mutate(group = "Age (years)"),
    
    "70 or older" = svytotal_df(design = subset(design, age >= 70), 
                                variables = var) %>% mutate(group = "Age (years)")
  ) %>% 
    {data.table(rbindlist(.) %>% select(-var),
                stratum = names(.) %>% rep(each = n_cats))} -> df
}

age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "male"), var = ~ new_1) %>% mutate(sex = "Male") -> age_male_new_1_df
age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "female"), var = ~ new_1) %>% mutate(sex = "Female") -> age_fem_new_1_df

age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "male"), var = ~ old_1) %>% mutate(sex = "Male") -> age_male_old_1_df
age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "female"), var = ~ old_1) %>% mutate(sex = "Female") -> age_fem_old_1_df

data.table(rbind(age_male_new_1_df %>% mutate(type = new_1_title),
                 age_fem_new_1_df %>% mutate(type = new_1_title), 
                 age_male_old_1_df %>% mutate(type = old_1_title), 
                 age_fem_old_1_df %>% mutate(type = old_1_title))) -> age_sex_df



age_sex_df[, sex := factor(sex, levels = c("Female", "Male"))]

```


##### Plot

```{r}

ggplot(
  data = age_sex_df[value == "yes" & stratum %nin% c("20-29")],
  aes(
    x = stratum,
    y = prop_pe,
    ymin = prop_lci,
    ymax = prop_uci,
    fill = type,
  )
) +
  #Geoms
  geom_col(width = 0.45, position = position_dodge(width = 0.5), lwd = 2) +
  geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
                position = position_dodge(width = 0.5)) +
  #Facet
  facet_wrap(~ sex, nrow = 1) +
  #Title
  ggtitle("Proportion of untreated US adults with a class I recommendation for pharmacotherapy, according to age and sex") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Age (years)") +
  scale_y_continuous(
    name = "Percent of Population (%)",
    labels = function(x) x * 100,
    breaks = seq(0, 100, 5)/100,
    sec.axis = dup_axis(name = NULL)
  ) +
  
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        strip.text = element_text(size = 18, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) -> age_cat_sex_fig

ggsave(age_cat_sex_fig,
       filename = "Figures/Age cat sex-stratified.pdf",
       dpi = 600, width = 16, height = 9)



```


#### Panel C [Race]

```{r}

ggplot(data = eligibility_df[value == "yes" & group %>% str_detect("Race")],
       aes(x = stratum, 
           y = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           fill = type)
) +
  #Geoms
  geom_col(width = 0.4, position = position_dodge(width = 0.5), lwd = 2) +
  geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
                position = position_dodge(width = 0.5)) +
  #Title
  ggtitle(label = "Proportion of untreated US adults with a class I recommendation for initiating LDL-C-lowering treatment, according to race/ethnicity") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Race and Ethnicity") +
  scale_y_continuous(name = "Percent of Population (%)",
                     labels = function(x) x * 100,
                     breaks = seq(0, 100, 5)/100,
                     sec.axis = dup_axis(name = NULL)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) +
  coord_cartesian(ylim = c(0, 0.35)) -> race_fig

ggsave(race_fig,
       filename = "Figures/Race and ethnicity.pdf",
       dpi = 600, width = 16, height = 9)

```

#### Panel D [Comorbidities]

```{r}
eligibility_df[, comorbidity_group := fcase(stratum %>% str_detect("Diabetes"), "Diabetes",
                                            stratum %>% str_detect("CKD"), "CKD",
                                            stratum %>% str_detect("Obesity"), "Obesity")]

ggplot(data = eligibility_df[stratum != "ASCVD" & value == "yes" & group %>% str_detect("Comorbidities") & str_detect(stratum, "No ", negate = T)],
       aes(x = stratum, 
           y = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           fill = type)
) +
  #Geoms
  geom_col(width = 0.4, position = position_dodge(width = 0.5), lwd = 2) +
  geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
                position = position_dodge(width = 0.5)) +
  facet_grid(. ~ comorbidity_group, scales = "free_x") +
  #Title
  ggtitle(label = "Proportion of untreated US adults with a class I recommendation for initiating LDL-C-lowering treatment, according to the presence/absence of comorbidities") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Presence or Absence of Comorbidity") +
  scale_y_continuous(name = "Percent of Population (%)",
                     labels = function(x) x * 100,
                     breaks = seq(0, 100, 5)/100,
                     sec.axis = dup_axis(name = NULL)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        strip.text = element_text(size = 18, face = "bold"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) +
  coord_cartesian(ylim = c(0, 0.85)) -> comorbidities_fig

ggsave(comorbidities_fig,
       filename = "Figures/Comorbidities.pdf",
       dpi = 600, width = 16, height = 9)

```

#### Combine A-D

##### Function

```{r}
rescale_ggplot <-
  theme(
  plot.title = element_text(size = 7, face = "bold", color = "transparent", hjust = 0),
  strip.text = element_text(size = 12, face = "bold"),
  plot.subtitle = element_blank(),
  axis.text.x = element_text(size = rel(0.9), face = "bold"),
  axis.text.y = element_text(size = rel(0.9), face = "bold"),
  axis.title.x = element_blank(),
  axis.title.y = element_text(size = rel(0.85), face = "bold"),
  axis.line = element_line(colour = "black", linewidth = 1.2),
  legend.key.width = unit(rel(2), "cm"),
  legend.key.height = unit(rel(0.5), "cm"),
  legend.text = element_text(size = rel(0.8), face = "bold")
  )

```

##### Combine

```{r}
library(ggpubr)
grid_2by2 <- function(width) {
  
  hrzl_coords = c(0.5, 0.5, 0, 1, 0, 1)
  vert_coords = c(0.04, 1, 0.52, 0.52, 0.04, 0.04)
  line_id = c(1, 1, 2, 2, 3, 3)
  grid.polygon(hrzl_coords, vert_coords, line_id, gp = gpar(lwd = width))
}

#Labels
fig1_labels <- c(
  "[A] Age",
  "[B] Age and Sex",
  "[C] Race and Ethnicity",
  "[D] Comorbidities"
) %>% paste0("   ", .)

#Plot
ggarrange(age_cat_fig + rescale_ggplot, 
          age_cat_sex_fig + rescale_ggplot,
          race_fig  + rescale_ggplot,
          comorbidities_fig + rescale_ggplot, 
          labels = fig1_labels,
          ncol = 2, nrow = 2,
          font.label = list(size = 13),
          common.legend = T,
          legend = "bottom",
          hjust = -0.01)

grid_2by2(width = 3)
fig1 <- grid.grab()
ggsave(fig1,
       filename = paste0("Figures/Figure 1.pdf"),
       device = cairo_pdf,
       width = 16,
       height = 9,
       dpi = 600)


```


##Plot I/II

#### Panel A [Age]

##### Calculate

```{r}



age_get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_1) -> age_new_1_df
age_get_svytotals(design = subset(sdata, llt == "no"), var = ~ old_1) -> age_old_1_df
age_get_svytotals(design = subset(sdata, llt == "no"), var = ~ new_12a) -> age_new_12a_df
age_get_svytotals(design = subset(sdata, llt == "no"), var = ~ old_12b) -> age_old_12b_df

rbind(age_old_1_df %>% mutate(type = old_1_title, class = "Class I"),
      age_new_1_df %>% mutate(type = new_1_title, class = "Class I"),
      age_old_12b_df %>% mutate(type = old_1_title, class = "Class II"),
      age_new_12a_df %>% mutate(type = new_1_title, class = "Class II")) %>%
  data.table -> age_12_df

age_12_df[, class_type := fcase(
  class == "Class I" & type %>% str_detect("2026"), "Class I by 2026 Guideline",
  class == "Class II" & type %>% str_detect("2026"), "Class II by 2026 Guideline",
  class == "Class I" & type %>% str_detect("2018"), "Class I by 2018 Guideline",
  class == "Class II" & type %>% str_detect("2018"), "Class II by 2018 Guideline"
)]
setorder(age_12_df, -class)

```


##### Plot

```{r}

ggplot(data = age_12_df[value == "yes" & stratum %nin% c("20-24", "25-29")],
       aes(x = stratum, 
           y = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           fill = class_type,
           group = type)) +
  #Geoms
  geom_col(width = 0.4, position = position_dodge(width = 0.5), lwd = 2) +
  # facet_grid2(. ~ stratum, scales = "free_x") +
  # geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
  #               position = position_dodge(width = 0.5)) +
  #Title
  ggtitle(label = "Proportion of untreated US adults with a class I/II recommendation for initiating LDL-C-lowering treatment, according to age") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Age (years)") +
  scale_y_continuous(name = "Percent of Population (%)",
                     labels = function(x) x * 100,
                     breaks = seq(0, 100, 5)/100,
                     expand = c(0, 0),
                     sec.axis = dup_axis(name = NULL)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm"),
        
      panel.border = element_rect(linewidth = 1.25),
      panel.spacing.x = unit(0, "pt"),
      strip.background.x = element_blank(), 
        strip.placement = "outside",
      strip.text.x = element_blank()
  ) +
  coord_cartesian(ylim = c(0, 1.03)) +
  guides(fill = guide_legend(nrow = 1)) -> age_cat_12_fig

ggsave(age_cat_12_fig,
       filename = "Figures/Age categorical [I and II].pdf",
       dpi = 600, width = 16, height = 9)

```



#### Panel B [Age/sex]

##### Calculate


```{r}

#12
age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "male"), var = ~ new_12a) %>% mutate(sex = "Male") -> age_male_new_12a_df
age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "female"), var = ~ new_12a) %>% mutate(sex = "Female") -> age_fem_new_12a_df
age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "male"), var = ~ old_12b) %>% mutate(sex = "Male") -> age_male_old_12b_df
age_sex_get_svytotals(design = subset(sdata, llt == "no" & sex == "female"), var = ~ old_12b) %>% mutate(sex = "Female") -> age_fem_old_12b_df

data.table(rbind(age_male_new_12a_df %>% mutate(type = new_1_title, class = "Class II"),
                 age_fem_new_12a_df %>% mutate(type = new_1_title, class = "Class II"), 
                 age_male_old_12b_df %>% mutate(type = old_1_title, class = "Class II"), 
                 age_fem_old_12b_df %>% mutate(type = old_1_title, class = "Class II"),
                 age_male_new_1_df %>% mutate(type = new_1_title, class = "Class I"),
                 age_fem_new_1_df %>% mutate(type = new_1_title, class = "Class I"), 
                 age_male_old_1_df %>% mutate(type = old_1_title, class = "Class I"), 
                 age_fem_old_1_df %>% mutate(type = old_1_title, class = "Class I")
                 )
           
           ) -> age_sex_12_df



age_sex_12_df[, sex := factor(sex, levels = c("Female", "Male"))]

#Class/type
age_sex_12_df[, class_type := fcase(
  class == "Class I" & type %>% str_detect("2026"), "Class I by 2026 Guideline",
  class == "Class II" & type %>% str_detect("2026"), "Class II by 2026 Guideline",
  class == "Class I" & type %>% str_detect("2018"), "Class I by 2018 Guideline",
  class == "Class II" & type %>% str_detect("2018"), "Class II by 2018 Guideline"
)]

```


##### Plot

```{r}

ggplot(
  data = age_sex_12_df[value == "yes" & stratum %nin% c("20-29")],
  aes(
    x = stratum,
    y = prop_pe,
    ymin = prop_lci,
    ymax = prop_uci,
    fill = class_type,
    group = type
  )
) +
  #Geoms
  geom_col(width = 0.45, position = position_dodge(width = 0.5), lwd = 2) +
  # geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
  #               position = position_dodge(width = 0.5)) +
  #Facet
  facet_wrap(~ sex, nrow = 1) +
  #Title
  ggtitle("Proportion of untreated US adults with a class I recommendation for pharmacotherapy, according to age and sex") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Age (years)") +
  scale_y_continuous(
    name = "Percent of Population (%)",
    labels = function(x) x * 100,
    breaks = seq(0, 100, 5)/100,
sec.axis = dup_axis(name = NULL)) +
  
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        strip.text = element_text(size = 18, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm"))  +
  guides(fill = guide_legend(nrow = 1))  -> age_cat_sex_12_fig

ggsave(age_cat_sex_12_fig,
       filename = "Figures/Age cat sex-stratified [I or II].pdf",
       dpi = 600, width = 16, height = 9)



```


#### Panel C [Race]

```{r}

#1/2
eligibility_df_1_2_sep_combined <- rbind(
  eligibility_df %>% filter(stratum != "ASCVD") %>% select(-stratum_group, - comorbidity_group) %>% mutate(class = "Class I"),
  eligibility_df_12 %>% mutate(class = "Class II")
)


#Class/type
eligibility_df_1_2_sep_combined[, class_type := fcase(
  class == "Class I" & type %>% str_detect("2026"), "Class I by 2026 Guideline",
  class == "Class II" & type %>% str_detect("2026"), "Class II by 2026 Guideline",
  class == "Class I" & type %>% str_detect("2018"), "Class I by 2018 Guideline",
  class == "Class II" & type %>% str_detect("2018"), "Class II by 2018 Guideline"
)]

#Reorder
eligibility_df_1_2_sep_combined[, class := fct_relevel(class, c("Class II", "Class I"))]
setorder(eligibility_df_1_2_sep_combined, class)

#Plot
ggplot(data = eligibility_df_1_2_sep_combined[value == "yes" & group %>% str_detect("Race")],
       aes(x = stratum, 
           y = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           fill = class_type,
           group = type)) +
  #Geoms
  geom_col(width = 0.4, position = position_dodge(width = 0.5), lwd = 2) +
  # geom_errorbar(width = 0.2, lwd = 1.25, color = "black",
  #               position = position_dodge(width = 0.5)) +
  #Title
  ggtitle(label = "Proportion of untreated US adults with a class I/II recommendation for initiating LDL-C-lowering treatment, according to race/ethnicity") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Race and Ethnicity") +
  scale_y_continuous(name = "Percent of Population (%)",
                     labels = function(x) x * 100,
                     breaks = seq(0, 100, 5)/100,
                     sec.axis = dup_axis(name = NULL)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) +
  coord_cartesian(ylim = c(0, 0.45)) +
  guides(fill = guide_legend(nrow = 1)) -> race_12_fig

ggsave(race_12_fig,
       filename = "Figures/Race and ethnicity [I and II].pdf",
       dpi = 600, width = 16, height = 9)

```

#### Panel D [Comorbidities]

```{r}
eligibility_df_1_2_sep_combined[, comorbidity_group := fcase(stratum %>% str_detect("Diabetes"), "Diabetes",
                                            stratum %>% str_detect("CKD"), "CKD",
                                            stratum %>% str_detect("Obesity"), "Obesity")]



ggplot(data = eligibility_df_1_2_sep_combined[stratum != "ASCVD" & value == "yes" & stratum %>% str_detect("No ", negate = T) & group %>% str_detect("Comorbidities")],
       aes(x = interaction(stratum, type), 
           y = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           fill = class_type,
           group = class_type)
) +
  #Geoms
  geom_col(width = 0.4, lwd = 2, position = position_identity()) +
  # geom_errorbar(width = 0.2, lwd = 1.25, color = "black", position = "stack") +
  facet_grid(. ~ comorbidity_group, scales = "free_x")  +
  #Title
  ggtitle(label = "Proportion of untreated US adults with a class I/II recommendation for initiating LDL-C-lowering treatment, according to the presence/absence of comorbidities") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = "Presence or Absence of Comorbidity", labels = NULL) +
  scale_y_continuous(name = "Percent of Population (%)",
                     labels = function(x) x * 100,
                     breaks = seq(0, 100, 5)/100,
                     expand = c(0, 0),
                     sec.axis = dup_axis(name = NULL)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        strip.text = element_text(size = 18, face = "bold"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) +
  coord_cartesian(ylim = c(0, 0.92)) +
  guides(fill = guide_legend(nrow = 1)) -> comorbidities_12_fig

ggsave(comorbidities_12_fig,
       filename = "Figures/Comorbidities [I or II].pdf",
       dpi = 600, width = 16, height = 9)


```

#### Combine A-D
```{r}
library(ggpubr)
grid_2by2 <- function(width) {
  
  hrzl_coords = c(0.5, 0.5, 0, 1, 0, 1)
  vert_coords = c(0.04, 1, 0.52, 0.52, 0.04, 0.04)
  line_id = c(1, 1, 2, 2, 3, 3)
  grid.polygon(hrzl_coords, vert_coords, line_id, gp = gpar(lwd = width))
}

#Labels
fig1_labels <- c(
  "[A] Age",
  "[B] Age and Sex",
  "[C] Race and Ethnicity",
  "[D] Comorbidities"
) %>% paste0("   ", .)

#Plot
ggarrange(age_cat_12_fig + rescale_ggplot, 
          age_cat_sex_12_fig + rescale_ggplot,
          race_12_fig  + rescale_ggplot,
          comorbidities_12_fig + rescale_ggplot, 
          labels = fig1_labels,
          ncol = 2, nrow = 2,
          font.label = list(size = 13),
          common.legend = T,
          legend = "bottom",
          hjust = -0.01)

grid_2by2(width = 3)
fig2 <- grid.grab()
ggsave(fig2,
       filename = paste0("Figures/Figure 2.pdf"),
       device = cairo_pdf,
       width = 16,
       height = 9,
       dpi = 600)


```



##Tabulate

```{r}



#Base
list_t1_base <- list(title = "Table 1. US adults not currently taking LDL-C-lowering medications eligible for pharmacological treatment, according to the 2018 and 2026 ACC/AHA Guidelines.",
                new = new_1_df,
                old = old_1_df,
                diff = abs_diff_init_df,
                name = "Table 1"
                )

#A1c
list_t1_a1c <- list(title = "Supplementary Table XXX [Redundant]. US adults not currently taking LDL-C-lowering medications eligible for pharmacological treatment, according to the 2018 and 2026 ACC/AHA Guidelines (using HbA1c for PREVENT).",
                new = new_1_df_a1c,
                old = old_1_df,
                diff = abs_diff_init_df_a1c,
                name = "Supplementary Table XXX [Redundant]"
                )
#UACR
list_t1_uacr <- list(title = "Supplementary Table XXX [Redundant]. US adults not currently taking LDL-C-lowering medications eligible for pharmacological treatment, according to the 2018 and 2026 ACC/AHA Guidelines (using UACR for PREVENT).",
                new = new_1_df_uacr,
                old = old_1_df,
                diff = abs_diff_init_df_uacr,
                name = "Supplementary Table XXX [Redundant]"
                )

#A1c/UACR
list_t1_uacr_a1c <- list(title = "Supplementary Table 6. US adults not currently taking LDL-C-lowering medications eligible for pharmacological treatment, according to the 2018 and 2026 ACC/AHA Guidelines (using HbA1c and UACR for PREVENT).",
                new = new_1_df_uacr_a1c,
                old = old_1_df,
                diff = abs_diff_init_df_uacr_a1c,
                name = "Supplementary Table 6"
                )


#Combined 1 and 2
list_t1_12 <- list(title = "Table 2. US adults not currently taking LDL-C-lowering medications eligible for pharmacological treatment, according to the 2018 and 2026 ACC/AHA Guidelines (additionally including class II recommendations with risk thresholds of 5-7.5% and 3-5% using the PCEs and PREVENT-ASCVD respectively).",
                new = new_12a_df,
                old = old_12b_df,
                diff = abs_diff_init_df_12,
                name = "Table 2"
                )

list_t1_2 <- list(title = "Supplementary Table XXX [Redundant]. US adults not currently taking LDL-C-lowering medications eligible for pharmacological treatment, according to the 2018 and 2026 ACC/AHA Guidelines (including only class II recommendations with risk thresholds of 5-7.5% and 3-5% using the PCEs and PREVENT-ASCVD respectively).",
                new = new_2a_df,
                old = old_2b_df,
                diff = abs_diff_init_df_2,
                name = "Supplementary Table XXX [Redundant]"
                )





t1_lists <- list(list_t1_base, list_t1_12, list_t1_2,
                 list_t1_a1c, list_t1_uacr, list_t1_uacr_a1c)

lapply(t1_lists, 
       function(t1_list) {
#Tabulate
cbind(
  #Old
  t1_list$old[value == "yes", .(`Variable` = group,
                            `Strata` = stratum,
                            `Proportion [95% CI], % ` = prop_pe_ci,
                            `Number [95% CI], millions ` = pe_ci)],
  #New, all
  t1_list$new[value == "yes", .(
                            `Proportion [95% CI], %  ` = prop_pe_ci,
                            `Number [95% CI], millions  ` = pe_ci)],
  t1_list$diff[, .(`Difference vs 2018 Guideline, % [95% CI] ` = prop_pe_ci,
                                    `Difference vs 2018 Guideline, millions [95% CI] ` = pe_ci
                                    )]
) %>%
  flextable %>%
  bold(j = c(1, 2)) %>%
  add_header_row(values = c(
    "",
    "Eligible for treatment by the 2018 ACC/AHA Guideline",
    "Eligible for treatment by the 2026 ACC/AHA Guideline",
    "Difference"
  ),
  colwidths = c(2, 2, 2, 2)
             ) %>%
  add_footer_row(values = as_paragraph(explanation_line), colwidths = 8) %>%
  add_footer_row(values = as_paragraph(abbs_line), colwidths = 8) %>%
  flextable_aes(table_title = t1_list$title) %>%
  merge_v() %>%
  fontsize(size = 9) %>%
  width(width = 0.9) -> t1_object
  save_as_docx(t1_object, path = paste0("Tables/", t1_list$name, ".docx"))
  
  t1_object
}) -> t1_t_list



```

##B. CACS

### Get numbers

```{r}

get_svytotals(design = subset(sdata, llt == "no"), var = ~ cacs_eligible) -> cacs_df


```


### Tabulate

```{r}
# flextable(cacs_df[value == "yes" & stratum %nin% c("Below 40", "ASCVD", "Diabetes"), 
#                   .(`Variable` = group,
#                             `Strata` = stratum,
#                             `Proportion [95% CI], %` = prop_pe_ci,
#                             `Number [95% CI], millions` = pe_ci)]) %>%
#   bold(j = c(1, 2)) %>%
#     add_footer_row(values = as_paragraph(explanation_line), colwidths = 4) %>%
#   flextable_aes(table_title = "Table 5. US adults not already on LDL-C-lowering therapy and potentially eligible for coronary artery calcium assessment per the 2026 ACC/AHA Dysylipidemia Guideline.") %>%
#   merge_v() %>%
#   add_footer_lines(values = as_paragraph(abbs_line)) -> cacs_t
#   save_as_docx(cacs_t, path = "Tables/Table 5.docx")

```


##C. Low-risk 10-year but high-risk longer term

### Get numbers

```{r}

sdata$variables[new_2a_ldl30 == "yes" & new_1 == "no", .(n = sum(weight)), by = age] -> long_short_df
long_short_df[order(age)] -> long_short_df
long_short_filler <- data.table(age = seq(20, 80), n = 0)
long_short_df <- rbind(long_short_df, long_short_filler[age %nin% long_short_df[, age]])

long_short_df[, cum_n := cumsum(n)]

#long_short_ages <- list(c(30, 39), c(40, 49), c(50, 59), c(30, 59))
long_short_ages <- list(c(30, 59), c(30, 34), c(35, 39), c(40, 44), c(45, 49), c(50, 54), c(55, 59))


sex_filters <- list(c("male"), c("female"), c("male", "female"))


#Loop over sex and age-groups
lapply(sex_filters, 
       function(sex_filter) {
#Loop over age-brackets
lapply(long_short_ages, 
       function(age_bracket) {
  
         
         filter_exp <- expression(age %between% age_bracket & prevent_10yr < 0.03 & sex %in% sex_filter & statin == "no" & new_1 == "no")
         #Total 2a
  svytotal_df(design = sdata %>% subset(eval(filter_exp)),
            variables = ~ new_2a_ldl30
            ) -> df_2a
    df_2a[, var := "Total number eligible based on LDL-C or 30-year risk"]
  
  #Total LDL > 160
  svytotal_df(design = sdata %>% subset(eval(filter_exp)),
            variables = ~ ldl > 160 & ldl <= 189
            ) -> df_ldl160
  df_ldl160[, var := "LDL between 160-189 mg/dL"]
  
  #Total high long-term risk
  svytotal_df(design = sdata %>% subset(eval(filter_exp)),
            variables = ~ prevent_30yr >= 0.1
            ) -> df_prevent30
  df_prevent30[, var := "30-year risk of 10% or greater"]
  
  #2a without 1a
  svytotal_df(design = sdata %>% subset(eval(filter_exp) & new_1 == "no" & statin == "no"),
            variables = ~ (age > 0)
            ) -> df_2a_only
  df_2a_only[, var := "Not using statins and no alternative class I indication"]
  
  #Bind
  rbind(df_2a, df_ldl160, df_prevent30, df_2a_only) -> combined_df
  
  #Add age
  combined_df[, age := paste0(age_bracket[1], " to ", age_bracket[2])]
  combined_df[, sex := ifelse(length(sex_filter) == 1, sex_filter %>% str_to_title, "Overall")]
  
  #Return
  combined_df
       }) 
         
       }
  
  ) -> new_2a_ldl30_df

new_2a_ldl30_df <- new_2a_ldl30_df %>% lapply(rbindlist) %>% rbindlist
new_2a_ldl30_df <- new_2a_ldl30_df[value %in% c("yes", T)]


#N in results
svytotal_df(design = subset(sdata, age %between% c(30, 59) & prevent_10yr < 0.03),
            variables = ~ (statin)) -> new_2a_ldl30_statin

svytotal_df(design = subset(sdata, age %between% c(30, 59) & prevent_10yr < 0.03 & statin == "no"),
            variables = ~ (new_1)) -> new_2a_ldl30_new_1

svytotal_df(design = subset(sdata, age %between% c(30, 59) & prevent_10yr < 0.03 & statin == "no" & new_1 == "no"),
            variables = ~ (age > 0)) -> new_2a_ldl30_total_n 

new_2a_ldl30_df[sex == "Overall" & age == "30 to 59"]
new_2a_ldl30_df[sex %in% c("Male", "Female") & str_detect(var, "Total") & age == "55 to 59"]

```

### Plot

```{r}

new_2a_ldl30_df[, age := fct_relevel(age, c("30 to 34", "35 to 39", "40 to 44", "45 to 49", "50 to 54", "55 to 59"))]
new_2a_ldl30_df[, var_2 := fifelse(var %in% 
                               c("LDL between 160-189 mg/dL",
                                 "Total number eligible based on LDL-C or 30-year risk"),
                             1,
                             fifelse(var == "Not using statins and no alternative class I indication", 2, NA)
)]

new_2a_ldl30_df[, sex := fct_relevel(sex, c("Overall", "Female", "Male"))]
new_2a_ldl30_df[, var := fct_relevel(var,
                               c("Not using statins and no alternative class I indication",
                               "Total number eligible based on LDL-C or 30-year risk",
                               "LDL between 160-189 mg/dL"))]
new_2a_ldl30_df 
new_2a_ldl30_df[, var2 := fcase(var == "Not using statins and no alternative class I indication", "Not eligible",
                          var == "Total number eligible based on LDL-C or 30-year risk", "30-year PREVENT-ASCVD risk ≥10%",
                          var == "LDL between 160-189 mg/dL", "LDL between 160-189 mg/dL"
                          )]
new_2a_ldl30_df[, var2 := fct_relevel(var2, c("LDL between 160-189 mg/dL", "30-year risk of 10% or greater", "Not eligible"))]
setorder(new_2a_ldl30_df, sex, age, var)


library(ggh4x)
new_2a_ldl30_df[var == "Total number eligible based on LDL-C or 30-year risk", 
          .(part = pe,
            age = age),
          by = sex] -> new_2a_ldl30_df_part

new_2a_ldl30_df[var == "Not using statins and no alternative class I indication", 
          .(total = pe, age),
          by = sex] -> new_2a_ldl30_df_total

merge(new_2a_ldl30_df_part, new_2a_ldl30_df_total[age != "30 to 59"]) -> new_2a_ldl30_df_prop
new_2a_ldl30_df_prop[, prop := part/total]
new_2a_ldl30_df_prop[, prop_scaled := rescale(prop, to = total %>% range, from = prop %>% range)]

new_2a_ldl30_df[var == "Not using statins and no alternative class I indication", pe, by = sex]



ggplot(data = new_2a_ldl30_df[age != "30 to 59" & var != "30-year risk of 10% or greater"],
       aes(x = age, 
           y = pe,
           ymin = lci,
           ymax = uci,
           fill = var2)
) +
  #Geoms
  geom_col(width = 0.8, alpha = 1, position = position_identity(), lwd = 2) +
  geom_line(data = new_2a_ldl30_df_prop[age != "30 to 59"], inherit.aes = F, lwd = 1.5,
            aes(x = age, y = prop_scaled, group = sex)
            ) +
  geom_point(data = new_2a_ldl30_df_prop[age != "30 to 59"], inherit.aes = F, size = 4,
            aes(x = age, y = prop_scaled, group = sex)
  ) +
  
  geom_text(data = new_2a_ldl30_df_prop[age != "30 to 59"], inherit.aes = F, size = 5, fontface = "bold",
            aes(x = age, y = prop_scaled, group = sex, label = percent(prop, 0.1), 
                hjust = 1, vjust = -0.8)) +
  # geom_errorbar(data =  new_2a_ldl30_df[var %in% c("Total number eligible based on LDL-C or 30-year risk", "Not using statins and no alternative class I indication")],
  #               aes(ymin = lci,
  #                   ymax = uci),
  #               width = 0.2, lwd = 1.25, color = "black") +
  facet_nested(. ~ sex, scales = "free") +
  #Title
  #ggtitle("Number of persons with a low short-term risk eligible based on an LDL-C 160-189 mg/dL or a 30-year risk of 10% or higher") +
  #Scales
  scale_fill_jama(name = NULL) +
  scale_x_discrete(name = NULL, labels = function(x) x %>% str_replace(" to ", "-")) +
  scale_y_continuous(name = "Number of US adults, in millions",
                     labels = function(x) x/1000000,
                     breaks = seq(1000000, 100000000, 2000000),
                     sec.axis = sec_axis(trans = ~ rescale(., from = new_2a_ldl30_df_prop$total %>% range, to = new_2a_ldl30_df_prop$prop %>% range), 
                                         name = "% of Adults in the Age Group Recommended for Statins (IIa)",
                                         labels = function(x) x * 100,
                                         breaks = seq(0, 100, 5)/100)
  ) +
  theme_bw() +
  theme(title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        strip.text = element_text(size = 18, face = "bold"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 13, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 15, face = "bold"),
        legend.key.width = unit(3, "cm")
  ) +
  guides(fill = guide_legend(nrow = 1)) -> fig4

ggsave(fig4,
       filename = "Figures/Figure 4.pdf",
       device = cairo_pdf,
       dpi = 600, width = 16, height = 9)


```


### Mid-aged & sex Simple bars

####Calculate

```{r}
#Age-sex primary prevention filter:
age_sex_filter <- expression(llt == "no" & age %between% c(40, 65) & ascvd == "no" & ldl < 190 & dm == "no")


##Proportions
#Female/prevent
svytotal_df(design = subset(sdata, eval(age_sex_filter) & sex == "female"  & egfr >= 60),
            variables = ~ new_1) -> mid_aged_fem_new_prop
#Male/prevent
svytotal_df(design = subset(sdata, eval(age_sex_filter) & sex == "male"  & egfr >= 60),
            variables = ~ new_1) -> mid_aged_male_new_prop


#Female/PCE
svytotal_df(design = subset(sdata, eval(age_sex_filter) & sex == "female"),
            variables = ~ old_1) -> mid_aged_fem_old_prop
#Male/PCE
svytotal_df(design = subset(sdata, eval(age_sex_filter) & sex == "male"),
            variables = ~ old_1) -> mid_aged_male_old_prop


#Rbind
mid_aged_prop_df <- rbind(mid_aged_fem_new_prop %>% mutate(type = "PREVENT-based risk of 5% or more", sex = "Females"),
                       mid_aged_male_new_prop %>% mutate(type = "PREVENT-based risk of 5% or more", sex = "Males"),
                       mid_aged_fem_old_prop %>% mutate(type = "PCE-based risk of 7.5% or more", sex = "Females"),
                       mid_aged_male_old_prop %>% mutate(type = "PCE-based risk of 7.5% or more", sex = "Males"))


```




### Sex-based risk Histograms

####Plot

```{r}
#Create ratio of risks
sdata$variables[, pce_prevent_ratio := prevent_10yr/pce_10yr]
# svyquantile(design = sdata, ~ pce_prevent_ratio, quantiles = c(0.25, 0.5, 0.75)) -> ratio_qs
hist_filter <- expr(llt == "no" & age %between% c(40, 69) & egfr >= 60 & ascvd == "no" & ldl < 190 & dm == "no")

sdata$variables[eval(hist_filter), .(q = wtd.quantile(x = pce_prevent_ratio, weights = weight, c(0.25, 0.5, 0.75))), by = sex] -> ratio_qs

ratio_qs[, q_format := round(q, 2) %>% format(nsmall = 2)]

#Risks
sdata$variables[eval(hist_filter), 
                .(pce_qs = wtd.quantile(x = pce_10yr, weights = weight, c(0.25, 0.5, 0.75)),
                  prevent_qs = wtd.quantile(x = prevent_10yr, weights = weight, c(0.25, 0.5, 0.75))
                  ), 
                by = sex] -> risk_qs
risk_qs[, let(pce_qs_format = percent(pce_qs, 0.1))]
risk_qs[, let(prevent_qs_format = percent(prevent_qs, 0.1))]

#Risk differences
svyglm(design = sdata %>% subset(eval(hist_filter)),
       family = Gamma(link = "log"),
       formula = pce_prevent_ratio ~ 1 + sex
       ) %>% summary

#Create labels
males_label <- paste0("Median ratio: ", ratio_qs[sex == "male", q_format][2], "; IQR: ", ratio_qs[sex == "male", q_format][1], " to ", ratio_qs[sex == "male", q_format][3])
females_label <- paste0("Median ratio: ", ratio_qs[sex == "female", q_format][2], "; IQR: ", ratio_qs[sex == "female", q_format][1], " to ", ratio_qs[sex == "female", q_format][3])
label_size <- 5
males_ypos <- -2.8e06
females_ypos <- 2.9e06

#Plot
ggplot(data = sdata$variables[sex == "female" & eval(hist_filter)],
       aes(x = pce_prevent_ratio,
           y = after_stat(count),
           weight = weight
       )) +
  #Histograms
  geom_histogram(color = "black",lwd = 0.5,
                 binwidth = 0.05,
                 aes(fill = "Females")
  ) +
  geom_histogram(data = sdata$variables[sex == "male"  & eval(hist_filter)], 
                 inherit.aes = F,
                 binwidth = 0.05,
                 aes(y = - after_stat(count),
                     x = pce_prevent_ratio,
                     weight = weight,
                     fill = "Males"),
                 color = "black",lwd = 0.5
  ) +
  #Horizontal line
  geom_hline(yintercept = 0, lwd = 1.5) +
  #Geoms denoting median and IQR
  #Females
  geom_errorbarh(aes(xmin = ratio_qs[sex == "female", q][1],
                    xmax = ratio_qs[sex == "female", q][3],
                    y = females_ypos,
                    color = "Females"),
                 lwd = 1.25, height = 150000
                ) +
    geom_point(aes(x = ratio_qs[sex == "female", q][2],
                    y = females_ypos,
                    color = "Females"
                    ),
                  size = 5
                ) +
  #Males
    geom_errorbarh(aes(xmin = ratio_qs[sex == "male", q][1],
                    xmax = ratio_qs[sex == "male", q][3],
                    y = males_ypos,
                    color = "Males"),
                 lwd = 1.25, height = 150000
                ) +
    geom_point(aes(x = ratio_qs[sex == "male", q][2],
                    y = males_ypos,
                    color = "Males"
                    ),
                  size = 5
                ) +
  annotate(geom = "text",
           x = ratio_qs[sex == "male", q][2],
                    y = males_ypos*1.1,
           label = males_label,
           size = label_size,
           fontface = "bold"
           ) +
    annotate(geom = "text",
           x = ratio_qs[sex == "female", q][2],
                    y = females_ypos*1.1,
           label = females_label,
           size = label_size,
           fontface = "bold"
           ) +
  #Scales
  scale_fill_nejm(name = NULL,
                  breaks = c("Females", "Males")) +
  scale_color_nejm(name = NULL,
                  breaks = c("Females", "Males")) +
  scale_y_continuous(name = "Number of US Adults, N",
                     breaks = seq(-100000000, 100000000, 1e06) %>% Filter(., f = function(x) x != 0),
                     expand = c(0.03, 0),
                     labels = function(x) abs(x) %>% comma) +
  scale_x_continuous(name = "Ratio of 10-year ASCVD PREVENT-based risk to PCE-based risk",
                     breaks = c(0.5, 1, 2),
                     labels = c("0.5\n(Half the PCE-estimated risk)", "1.0\n(no change)", "2.0\n(double the PCE-estimated risk)"),
                     expand = c(0.01, 0),
                     trans = "log") +
  #Title
  #ggtitle("Ratio of PREVENT-based to PCE-based 10-year ASCVD risks in males and females aged 40-69 years") +
  #Theme
  theme_bw() +
  guides(fill = guide_legend(byrow = TRUE)) +
  theme(text = element_text(size = 23),
        plot.title=element_text(face = "bold",hjust = 0.0, size = 16),
        plot.subtitle = element_text(face = "bold", size = 12, hjust = 0.0, color = "grey45"),
        axis.text.x = element_text(size = 16, face = "bold"),
        axis.text.y = element_text(size = 16, face = "bold"),
        axis.title.x = element_text(size = 20, face = "bold"),
        axis.title.y = element_text(size = 20, face = "bold"),
        axis.line = element_line(colour = "black", linewidth = 1.2),
        plot.margin = margin(0.5, 1, 0.5, 1, "cm"),
        legend.position = c(0.85, 0.95),
        legend.key.width = unit(2, "cm"),
        legend.spacing.y = unit(8, 'lines'),
        legend.title = element_text(face = "bold"),
        legend.text = element_text(face = "bold"),
        legend.background = element_rect(fill = "transparent")
  ) +
  coord_cartesian(xlim = c(0.2, 3)) -> fig4



#Plot
ggsave(fig4,
       filename = "Figures/Figure 4.pdf",
       dpi = 600,
       width = 16, height = 9
)


```


##D. Eligible for intensification

#### Functions

##### Function for LDL categories

```{r}
#Experiment
#design = subset(sdata, eval(four_group_filters[[3]]) & llt == "yes"); var = ~ ldl_cat

#Function
get_svytotals_mod <- function(design = sdata, var, n_cats = 2) {
#Get total number of eligible patients (10%+) according to PREVENT
list(
  #Overall
  " " = svytotal_df(design = design, 
                    variables = var) %>% mutate(group = "Overall"),
  #Age-stratified
  "Below 65" = svytotal_df(design = subset(design, age < 65), 
                        variables = var) %>% mutate(group = "Age (years)"),
  "65 or older" = svytotal_df(design = subset(design, age >= 65), 
                        variables = var) %>% mutate(group = "Age (years)"),
  #Sex-stratified
  "Female" = svytotal_df(design = subset(design, sex == "female"), 
                         variables = var) %>% mutate(group = "Sex"),
  "Male" = svytotal_df(design = subset(design, sex == "male"), 
                       variables = var) %>% mutate(group = "Sex"),
  #Race-stratified
  "NH Black" = svytotal_df(design = subset(design,  race == "Non-Hispanic Black"), 
                           variables = var) %>% mutate(group = "Race and ethnicity"),
  "NH White" = svytotal_df(design = subset(design,  race == "Non-Hispanic White"), 
                           variables = var) %>% mutate(group = "Race and ethnicity"),
  "NH Asian" = svytotal_df(design = subset(design, race == "Non-Hispanic Asian"), 
                           variables = var) %>% mutate(group = "Race and ethnicity"),
  "Hispanic" = svytotal_df(design = subset(design, race == "Hispanic"), 
                           variables = var) %>% mutate(group = "Race and ethnicity")
) %>% 
  #Bind together
  {data.table(rbindlist(.) %>% select(-var),
              stratum = names(.) %>% rep(each = n_cats))} -> df
  
}


```

##### Function for goals

```{r}
#Experiment
#design = subset(sdata, eval(four_group_filters[[3]]) & llt == "yes"); var = ~ ldl_cat

eight_groups <- c(
  expression(ascvd == "yes" & vh_risk_ascvd == "no"),
  expression(vh_risk_ascvd == "yes"),
  expression(dm == "yes" & rf_enhancers_2026 == "yes"),
  expression(dm == "yes" & rf_enhancers_2026 == "no")
)


#Function
get_svytotals_goals <- function(design = sdata, var, n_cats = 2) {
#Get total number of eligible patients (10%+) according to PREVENT
list(
  #Overall
  " " = svytotal_df(design = design, 
                    variables = var) %>% mutate(group = "Overall"),
  #Age-stratified
  "Below 65" = svytotal_df(design = subset(design, vh_risk_ascvd == "yes"), 
                        variables = var) %>% mutate(group = "Age (years)"),
  "65 or older" = svytotal_df(design = subset(design, age >= 65), 
                        variables = var) %>% mutate(group = "Age (years)"),
  #Sex-stratified
  "Female" = svytotal_df(design = subset(design, sex == "female"), 
                         variables = var) %>% mutate(group = "Sex"),
  "Male" = svytotal_df(design = subset(design, sex == "male"), 
                       variables = var) %>% mutate(group = "Sex"),
  #Race-stratified
  "NH Black" = svytotal_df(design = subset(design,  race == "Non-Hispanic Black"), 
                           variables = var) %>% mutate(group = "Race and ethnicity"),
  "NH White" = svytotal_df(design = subset(design,  race == "Non-Hispanic White"), 
                           variables = var) %>% mutate(group = "Race and ethnicity"),
  "NH Asian" = svytotal_df(design = subset(design, race == "Non-Hispanic Asian"), 
                           variables = var) %>% mutate(group = "Race and ethnicity"),
  "Hispanic" = svytotal_df(design = subset(design, race == "Hispanic"), 
                           variables = var) %>% mutate(group = "Race and ethnicity")
) %>% 
  #Bind together
  {data.table(rbindlist(.) %>% select(-var),
              stratum = names(.) %>% rep(each = n_cats))} -> df
  
}


```


###LDL

##### Get numbers

```{r}
#LDL weights
sdata_ldl <- svydesign(data = data,
                       ids = data$SDMVPSU,
                       strata = data$SDMVSTRA,
                       weights = data$weight_ldl,
                       nest = TRUE)
sdata_ldl <- subset(sdata_ldl, age >= 20 & llt == "yes" & new_1 == "yes")


#Total
get_svytotals_mod(design = subset(sdata_ldl, new_1 == "yes"),
              var = ~ goal_need_ldl, 
              n_cats = 4) -> goal_need_ldl_cat_df

#Using LLT
four_group_filters <- c(expr(ascvd == "yes"), 
                        expr(dm == "yes" & ascvd == "no"), 
                        expr(pre_ttt_ldl >= 190 & dm == "no" & ascvd == "no"),
                        expr(new_1 == "yes" & pre_ttt_ldl < 190 & dm == "no" & ascvd == "no")
                        )

#Loop over 4 groups
lapply(
  four_group_filters[1:4],
  function(group_filter) {
    get_svytotals_mod(design = subset(sdata_ldl, eval(group_filter) & llt == "yes"),
              var = ~ ldl_cat, 
              n_cats = 4)
    
  }
) -> llt_ldl_cat_list


names(llt_ldl_cat_list) <- c("ASCVD",
                                       "DM without ASCVD",
                                       "LDL-C of ≥190 mg/dL or greater without ASCVD or DM",
                                       "Primary prevention without DM, ASCVD, and pre-treatment LDL-C <190 mg/dL")


#N for results
llt_ldl_cat_list$`DM without ASCVD`[c(1, 2), prop_pe %>% sum %>% percent(0.1)]
llt_ldl_cat_list$ASCVD[c(1), prop_pe %>% sum %>% percent(0.1)]


#Loop
# lapply(
#   four_group_filters[1:4],
#   function(group_filter) {
#     get_svytotals_mod(design = subset(sdata, eval(group_filter) & llt == "yes"),
#               var = ~ goal_need_ldl, 
#               n_cats = 4)
#     
#   }
# ) -> llt_goal_need_ldl_cat_list
# 
# names(llt_goal_need_ldl_cat_list) <- c("ASCVD",
#                                        "DM without ASCVD",
#                                        "LDL-C of 190 mg/dL or greater without ASCVD or DM",
#                                        "PREVENT-based 10-year ASCVD risk of 5% or greater")

```

##### Plot [not used]

```{r}

#Palettes
palette_map <- c(
  "LDL-C <55 mg/dL" = "#CCEBC5",
  "LDL-C of 100 mg/dL or greater" = "#FBB4AE",
  "LDL-C 55-69 mg/dL" = "#B3CDE3",
  "LDL-C 70-99 mg/dL" = "#DECBE4"
)

#Loop
lapply(1:length(llt_ldl_cat_list),
       function(i) {
         
         #Assign df
         llt_ldl_cat_df <- llt_ldl_cat_list[[i]]
         #Modify for plotting
llt_ldl_cat_df[, stratum_group := interaction(stratum, group %>% paste0("."))]
llt_ldl_cat_df[stratum == " ", stratum := "Overall"]
llt_ldl_cat_df[stratum == "Overall", group := ""]
llt_ldl_cat_df[, stratum_group := factor(stratum_group,
                                         levels = llt_ldl_cat_df$stratum_group %>%
                                           unique %>% rev)]


llt_ldl_cat_df[, value := fct_relevel(value, c(
  "LDL-C <55 mg/dL",
                                "LDL-C 55-69 mg/dL",
                                "LDL-C 70-99 mg/dL",
                                "LDL-C of 100 mg/dL or greater" ))]

llt_ldl_cat_df[order(value)] -> llt_ldl_cat_df

#Create geom_text aestetics
llt_ldl_cat_df[, geom_text_pos := c(0, prop_pe[1], prop_pe[1] + prop_pe[2],  prop_pe[1] + prop_pe[2] + prop_pe[3]), 
              by = stratum]
llt_ldl_cat_df[, diff(geom_text_pos), by = stratum_group]

llt_ldl_cat_df[, diff(geom_text_pos)]
llt_ldl_cat_df[, geom_text_label := 
                paste0(percent(prop_pe, 1),
                       "\n", pe %>% tomil, "m")]
llt_ldl_cat_df[, geom_text_label := str_replace(geom_text_label, "0.0m", "<0.1m")]
llt_ldl_cat_df <- llt_ldl_cat_df[round(prop_pe*100) == 0, geom_text_label := ""]
llt_ldl_cat_df[, geom_text_pos := {
  x <- geom_text_pos
  space_adj = 0.05
  for (i in 2:.N) {
    if ( ((x[i] - x[i-1]) < 0.06) & x[i] > 0.01) {
      x[i] <- x[i-1] + 0.06
    }
  }
  x
}, by = stratum_group]


#llt_goal_need_ldl_cat_df[, value := droplevels(value)]
#llt_goal_need_ldl_cat_df[geom_text_label  %>% str_detect("0% \\[0"), geom_text_label := ""]
#llt_goal_need_ldl_cat_df[pe < 1e05 & prop_pe > 0.005, geom_text_label := paste0(percent(prop_pe, 1), " [", round(pe/1e6, 2), "m]")]
#Angles vector
angles_vector <- c(0)


label_size <- 5
#Plot
ggplot(data = llt_ldl_cat_df,
       aes(x = prop_pe,
           ymin = prop_lci,
           ymax = prop_uci,
           y = stratum_group,
           fill = value
           )) +
  geom_col(position = position_stack(reverse = T),
           width = 0.7,
           color = "black",
           show.legend = T) +
  geom_text(hjust = -0.1, fontface = "bold", size = 2.5,
            aes(x = geom_text_pos,
                label = geom_text_label)) +
  #Plot scales
    scale_y_discrete(name = NULL) +
  scale_x_continuous(name = "Proportion (%)",
                     breaks = seq(0, 1, 0.05),
                     expand = c(0, 0),
                     labels = function(x) (x * 100),
                     sec.axis = dup_axis(name = NULL)
                     ) +
  scale_fill_manual(name = NULL,
                    values = palette_map,
                    drop = F
                    ) +
  guides(y = legendry::guide_axis_nested(key = key_range_auto("\\."))) +
  #Title
  ggtitle(names(llt_ldl_cat_list)[i]) +
    theme_bw() +
    theme(title = element_text(size = 13, face = "bold"),
          plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 14, face = "bold"),
        axis.text.y = element_text(angle = angles_vector, size = 12, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 11, face = "bold"),
        legend.title = element_text(size = 17, face = "bold"),
        legend.key.width = unit(2, "cm")
        ) +
  coord_cartesian(
    xlim = c(0, 1.08)
  ) +
  guides(fill = guide_legend(nrow = 1)) -> intensification_prop_fig


#Predicted risks
ggsave(intensification_prop_fig,
       filename = paste0("Figures/Figure 5 [not used", LETTERS[i], "].pdf"),
       dpi = 600,
       width = 16, height = 9
       )

intensification_prop_fig
         
         
       }
       
       ) -> intensification_prop_fig_list

names(intensification_prop_fig_list) <- names(llt_ldl_cat_list)

```

##### Combine

```{r}
library(ggpubr)
grid_2by2 <- function(width) {
  
  hrzl_coords = c(0.5, 0.5, 0, 1, 0, 1)
  vert_coords = c(0.04, 1, 0.52, 0.52, 0.04, 0.04)
  line_id = c(1, 1, 2, 2, 3, 3)
  grid.polygon(hrzl_coords, vert_coords, line_id, gp = gpar(lwd = width))
}

#Labels
fig5_labels <- paste0("[", LETTERS[1:4], "] ", names(llt_ldl_cat_list))

#Plot
ggarrange(intensification_prop_fig_list$ASCVD + rescale_ggplot, 
          intensification_prop_fig_list$`DM without ASCVD` + rescale_ggplot,
          intensification_prop_fig_list$`LDL-C of 190 mg/dL or greater without ASCVD or DM`  + rescale_ggplot,
          intensification_prop_fig_list$`PREVENT-based 10-year ASCVD risk of 5% or greater` + rescale_ggplot, 
          labels = fig5_labels,
          ncol = 2, nrow = 2,
          font.label = list(size = 13),
          common.legend = T,
          legend = "bottom",
          hjust = -0.01)

grid_2by2(width = 3)
fig5_unused <- grid.grab()
ggsave(fig5_unused,
       filename = paste0("Figures/Figure 5 [unused].pdf"),
       device = cairo_pdf,
       width = 16,
       height = 9,
       dpi = 600)


```


##### Plot [used]

```{r}

#Collate in single df
lapply(1:length(llt_ldl_cat_list), 
       function(i) llt_ldl_cat_list[[i]][1:4,] %>% mutate(type = names(llt_ldl_cat_list)[i])) %>%
  rbindlist -> llt_ldl_cat_overall_df

#Reorder levels
llt_ldl_cat_overall_df[, value := fct_relevel(value, c(
  "LDL-C <55 mg/dL",
  "LDL-C 55-69 mg/dL",
  "LDL-C 70-99 mg/dL",
  "LDL-C of 100 mg/dL or greater" ))]

llt_ldl_cat_overall_df[order(value)] -> llt_ldl_cat_overall_df

#Create geom_text aestetics
llt_ldl_cat_overall_df[, geom_text_pos := c(0, prop_pe[1], prop_pe[1] + prop_pe[2],  prop_pe[1] + prop_pe[2] + prop_pe[3]), 
               by = type]
llt_ldl_cat_overall_df[, diff(geom_text_pos), by = type]

llt_ldl_cat_overall_df[, diff(geom_text_pos)]
llt_ldl_cat_overall_df[, geom_text_label := 
                 paste0(percent(prop_pe, 0.1),
                        " (", pe %>% tomil, "m)")]
llt_ldl_cat_overall_df[, geom_text_label := str_replace(geom_text_label, "0.0m", "<0.1m")]
llt_ldl_cat_overall_df <- llt_ldl_cat_overall_df[round(prop_pe*100) == 0, geom_text_label := ""]
llt_ldl_cat_overall_df[, geom_text_pos := {
  x <- geom_text_pos
  space_adj = 0.05
  for (i in 2:.N) {
    if ( ((x[i] - x[i-1]) < 0.06) & x[i] > 0.01) {
      x[i] <- x[i-1] + 0.06
    }
  }
  x
}, by = type]

llt_ldl_cat_overall_df[, geom_text_pos := cumsum(prop_pe) - prop_pe / 2, by = .(type)]

#llt_goal_need_ldl_cat_df[, value := droplevels(value)]
#llt_goal_need_ldl_cat_df[geom_text_label  %>% str_detect("0% \\[0"), geom_text_label := ""]
#llt_goal_need_ldl_cat_df[pe < 1e05 & prop_pe > 0.005, geom_text_label := paste0(percent(prop_pe, 1), " [", round(pe/1e6, 2), "m]")]
#Angles vector
angles_vector <- c(0)


label_size <- 5

#Wrap text for fit
llt_ldl_cat_overall_df[, type_wrap := str_wrap(type, width = 40)]
#Plot
ggplot(data = llt_ldl_cat_overall_df,
       aes(y = prop_pe,
           x = type,
           fill = value
       )) +
  geom_col(position = position_stack(reverse = T),
           width = 0.7,
           color = "black",
           show.legend = T) +
  geom_text(vjust = -0.1, fontface = "bold", size = 7,
            aes(y = geom_text_pos,
                label = geom_text_label)) +
  facet_grid(. ~ type_wrap, scales = "free") +
  #Plot scales
  scale_x_discrete(name = NULL, labels = NULL) +
  scale_y_continuous(name = "Proportion (%)",
                     breaks = seq(0, 1, 0.05),
                     expand = c(0, 0),
                     labels = function(x) (x * 100),
                     sec.axis = dup_axis(name = NULL)
  ) +
  scale_fill_manual(name = NULL,
                    values = palette_map,
                    drop = F
  ) +
  #Title
  ggtitle(NULL) +
  theme_bw() +
  theme(title = element_text(size = 13, face = "bold"),
        plot.subtitle = element_text(face = "bold", size = 11, hjust = 0.0, color = "grey45"),
        text = element_text(size = 14, face = "bold"),
        axis.title.x = element_text(size = 18, face = "bold"),
        axis.title.y = element_text(size = 18, face = "bold"),
        axis.text.x = element_text(size = 14, face = "bold"),
        axis.text.y = element_text(angle = angles_vector, size = 12, face = "bold"),
        legend.position = "bottom",
        legend.key = element_rect(fill = "transparent"),
        legend.background = element_rect(fill = "transparent"),
        legend.text = element_text(size = 14, face = "bold"),
        legend.title = element_text(size = 17, face = "bold"),
        legend.key.width = unit(3, "cm"),
        strip.text = element_text(size = 12, face = "bold")
  ) +
  coord_cartesian(
    ylim = c(0, 1.08)
  ) +
  guides(fill = guide_legend(nrow = 1)) -> fig5


#Predicted risks
ggsave(fig5,
       filename = paste0("Figures/Figure 5.pdf"),
       dpi = 600,
       device = cairo_pdf,
       width = 16, height = 9
)




```


###Total LDL-C/non-HDL-C

#####Calculate

```{r}
get_svytotals_mod(design = subset(sdata, new_1 == "yes"),
              var = ~ goal_need, 
              n_cats = 4) -> goal_need_cat_df

```


#####Tabulate

```{r}

goal_need_cat_df[, prop_pe_ci := make_prop_pe_ci(prop_pe, prop_lci, prop_uci)]
goal_need_cat_df[, prop_pe_ci_pct := make_prop_pe_ci_pct(prop_pe, prop_lci, prop_uci)]
goal_need_cat_df[, prop_pe_ci_pct := make_prop_pe_ci_pct(prop_pe, prop_lci, prop_uci)]
goal_need_cat_df[, pe_ci := make_pe_ci_mil(pe, lci, uci)]

goal_need_cat_df[, stratum := fct_relevel(stratum, levels = unique(goal_need_cat_df$stratum))]
goal_need_cat_df <- goal_need_cat_df[order(stratum)]
flextable(goal_need_cat_df[, .(`Variable` = group,
                            `Strata` = stratum,
                            `Category` = value,
                            `Proportion [95% CI], %` = prop_pe_ci,
                            `Number [95% CI], millions` = pe_ci)]) %>%
  bold(j = c(1, 2)) %>%
  
    add_footer_row(values = as_paragraph("LDL-C: Low-density lipoprotein cholesterol; Non-HDL-C: Non-high-density lipoprotein cholesterol; NH: Non-Hispanic"),
                 colwidths = 5) %>%
  flextable_aes(table_title = "Supplementary Table XXX [Redundant] Goal attainment of low-denisty and non-high-density lipoprotein cholesterol among US adults with a class I treatment indication per the 2026 ACC/AHA Dysylipidemia Guideline (including those yet to initiate pharmacotherapy).") %>%
  merge_v() %>%
  add_footer_lines(values = as_paragraph(abbs_line)) -> goal_need_cat_t
  save_as_docx(goal_need_cat_t, path = "Tables/Supplementary Table XXX [Redundant].docx")
  

```

###Tabulate LDL/non-HDL eligiblity

```{r}


#Three treatment goals
three_groups <- c(
  "Goal LDL-C/non-HDL-C <55/85 mg/dL" = expression(goal_55_85 == 1),
  "Goal LDL-C/non-HDL-C <70/100 mg/dL" = expression(goal_55_85 == 0 & goal_70_100 == 1),
  "Goal LDL-C/non-HDL-C <100/130 mg/dL" = expression(goal_55_85 == 0 & goal_70_100 == 0 & goal_100_130 == 1)
)

#Loop
lapply(1:length(three_groups),
       function(i) {
         svytotal_df(design = subset(sdata, eval(three_groups[[i]]) & llt == "yes"),
                     var = ~ goal_need_ldl_non_hdl
         ) -> df
         
         df[, goal := names(three_groups[i])]
         
         df[, n_respondents := subset(sdata, eval(three_groups[[i]]) & llt == "yes")$variables[, .N]]
       }
) %>%
  rbindlist -> goal_need_ldl_non_hdl_df

#Relevel factors
goal_need_ldl_non_hdl_df[, value := fct_relevel(
  value,
  c("Meets both LDL-C and non-HDL-C goal",
    "Meets LDL-C but not non-HDL-C goal",
    "Does not meet LDL-C goal")
)]
goal_need_ldl_non_hdl_df[, goal := fct_relevel(goal, 
                                       "Goal LDL-C/non-HDL-C <100/130 mg/dL",
                                       "Goal LDL-C/non-HDL-C <70/100 mg/dL",
                                       "Goal LDL-C/non-HDL-C <55/85 mg/dL")]
#Reorder
setorder(goal_need_ldl_non_hdl_df, goal, value)

#Tabulate
flextable(goal_need_ldl_non_hdl_df[, .(`Treatment goal` = goal,
                                       `Respondents, N` = n_respondents,
                                        `Goal Attainment` = value,
                                        `Proportion [95% CI], %` = prop_pe_ci,
                                        `Number [95% CI], millions` = pe_ci)]) %>%
  bold(j = c(1, 2)) %>%
    add_footer_row(values = as_paragraph("LDL-C: Low-density lipoprotein cholesterol; Non-HDL-C: Non-high-density lipoprotein cholesterol"),
                 colwidths = 5) %>%
  flextable_aes(table_title = "Supplementary Table XXX [Redundant] Goal attainment of low-density and non-high-density lipoprotein cholesterol among US adults with a class I treatment indication per the 2026 ACC/AHA Dysylipidemia Guideline among those on pharmacotherapy, stratified by treatment goal.") %>%
  merge_v() %>%
  add_footer_lines(values = as_paragraph(abbs_line)) -> goal_need_ldl_non_hdl_t
  save_as_docx(goal_need_ldl_non_hdl_t, path = "Tables/Supplementary Table XXX [Redundant].docx")




```

#### Tabulate LDL/ApoB

```{r}

#Use ApoB weights to create survey object
sdata_apo_b <- svydesign(data = data,
                       ids = data$SDMVPSU,
                       strata = data$SDMVSTRA,
                       weights = data$weight_apob,
                       nest = TRUE)


#Three treatment goals
three_groups <- c(
  "Goal LDL-C/apoB goal <55/55 mg/dL " = expression(goal_55_85 == 1),
  "Goal LDL-C/apoB <70/70 mg/dL" = expression(goal_55_85 == 0 & goal_70_100 == 1),
  "Goal LDL-C/apoB <100/90 mg/dL" = expression(goal_55_85 == 0 & goal_70_100 == 0 & goal_100_130 == 1)
)

#Three treatment goals
#Loop
lapply(1:length(three_groups),
       function(i) {
         svytotal_df(design = subset(sdata, eval(three_groups[[i]]) & llt == "yes"),
                     var = ~ goal_need_ldl_apo_b
         ) -> df
         
         df[, goal := names(three_groups[i])]
         
         df[, n_respondents := subset(sdata, eval(three_groups[[i]]) & llt == "yes")$variables[, .N]]
       }
) %>%
  rbindlist -> goal_need_ldl_apo_b_df

#Relevel factors
goal_need_ldl_apo_b_df[, value := fct_relevel(
  value,
  c("Meets both LDL-C and apoB goal",
    "Meets LDL-C but not apoB goal",
    "Does not meet LDL-C goal")
)]

#Reorder
setorder(goal_need_ldl_apo_b_df, goal, value)

#Tabulate
flextable(goal_need_ldl_apo_b_df[, .(`Treatment goal` = goal,
                                       `Respondents, N` = n_respondents,
                                       
                                       `Goal Attainment` = value,
                                       `Proportion [95% CI], %` = prop_pe_ci,
                                       `Number [95% CI], millions` = pe_ci)]) %>%
  bold(j = c(1, 2)) %>%
  add_footer_row(values = as_paragraph("LDL-C: Low-density lipoprotein cholesterol; apoB: Apolipoprotein B"),
                 colwidths = 5) %>%
  flextable_aes(table_title = "Supplementary Table XXX [Redundant]. Goal attainment of low-density and apoB among US adults with a class I treatment indication per the 2026 ACC/AHA Dysylipidemia Guideline among those on pharmacotherapy, stratified by treatment goal.") %>%
  merge_v() %>%
  add_footer_lines(values = as_paragraph(abbs_line)) -> goal_need_ldl_apo_b_t
  save_as_docx(goal_need_ldl_apo_b_t, path = "Tables/Supplementary Table XXX [Redundant].docx")

```

#### Tabulate LDL/non-HDL-C/ApoB


```{r}

#Use ApoB weights to create survey object
sdata_apo_b <- svydesign(data = data,
                       ids = data$SDMVPSU,
                       strata = data$SDMVSTRA,
                       weights = data$weight_apob,
                       nest = TRUE)
sdata_apo_b <- subset(sdata_apo_b, age >= 20 & llt == "yes" & new_1 == "yes")


#Three treatment goals
three_groups <- c(
  "Overall" = expression(new_1 == "yes"),
  "Goal LDL-C/non-HDL-C/apoB goal <55/85/55 mg/dL" = expression(goal_55_85 == 1 & new_1 == "yes"),
  "Goal LDL-C/non-HDL-C/apoB <70/100/70 mg/dL" = expression(goal_55_85 == 0 & goal_70_100 == 1 & new_1 == "yes"),
  "Goal LDL-C/non-HDL-C/apoB <100/130/90 mg/dL" = expression(goal_55_85 == 0 & goal_70_100 == 0 & goal_100_130 == 1 & new_1 == "yes")
)

#Three treatment goals
#Loop
lapply(1:length(three_groups),
       function(i) {
         svytotal_df(design = subset(sdata_apo_b, eval(three_groups[[i]]) & llt == "yes"),
                     var = ~ goal_need_3
         ) -> df
         
         
         
         #Merge to add N of respondents
         merge(df,
               subset(sdata_apo_b, eval(three_groups[[i]]) & llt == "yes")$variables[, .(n_respondents = .N), by = goal_need_3], 
               
               by.y = "goal_need_3", by.x = "value"
               ) -> df
         
         #Add N of adults
         df[, n_adults := pe %>% comma]
         
         #Totals
         df[, total_n_respondents := subset(sdata_apo_b, eval(three_groups[[i]]) & llt == "yes")$variables[, .N]]
         df[, total_n_adults := subset(sdata_apo_b, eval(three_groups[[i]]) & llt == "yes")$variables[, sum(weight_apob) %>% comma]]
         
         
         #Missing rows
         if(nrow(df) < 4) {
           data.table(var = "goal_need_3",
                      value = data[,  unique(goal_need_3 %>% na.omit)[unique(goal_need_3 %>% na.omit) %nin% df$value]],
                                     pe = 0, lci = 0, uci = 0,
                                     prop_pe = 0, prop_lci = 0, prop_uci = 0, pe_ci = 0, prop_pe_ci = 0, prop_pe_ci_pct = 0, n_adults = 0, n_respondents = 0,
                      total_n_respondents = 0, total_n_adults = 0) -> add_df
          
           df <- rbind(df, add_df) 
         }
         
         
         
         
         #Gaol
         df[, goal := names(three_groups[i])]
         
         df
       }
) %>%
  rbindlist -> goal_need_3_df

#Relevel factors
goal_need_3_df[, value := fct_relevel(
  value,
  c("Meets LDL-C, non-HDL-C, and apoB goals",
    "Meets LDL-C and non-HDL-C but not apoB goal",
    "Meets LDL-C but not non-HDL-C goal" ,
    "Does not meet LDL-C goal")
)]

goal_need_3_df[, goal := fct_relevel(
  goal,
  c("Overall",
    goal_need_3_df[goal != "Overall", unique(goal)])
)]

#Reorder
setorder(goal_need_3_df, goal, -value)

#Tabulate
flextable(goal_need_3_df[, .(`Treatment goal` = goal,
                                       `Goal Attainment` = value,
                              `Number of Respondents` = n_respondents,
                             `Number of US adults` = n_adults,
                                       
                                       `Proportion [95% CI], %` = prop_pe_ci,
                                       `Number [95% CI], millions` = pe_ci)]) %>%
  bold(j = c(1, 2)) %>%
    merge_v() %>%
  add_footer_row(values = as_paragraph("LDL-C: Low-density lipoprotein cholesterol; non-HDL-C: non-high-density lipoprotein cholesterol; apoB: Apolipoprotein B"),
                 colwidths = 6) %>%
  footnote(i = 5, j = 1, ref_symbols = "*",  
           value = as_paragraph("Includes class I indications for patients with a PREVENT-based score of 5 to 10% and DM  or pre-treatment LDL ≥190mg/dL without risk-enhancing factors.")) %>%
    footnote(i = 9, j = 1, ref_symbols = "**",  
           value = as_paragraph("Includes class I indications for patients with a PREVENT-based score of ≥10%, DM or pre-treatment LDL ≥190mg/dL with risk-enhancing factors, or ASCVD that is not at very high risk.")) %>%
      footnote(i = 13, j = 1, ref_symbols = "***",  
           value = as_paragraph("Includes class I indications for patients with ASCVD at very high risk.")) %>%
  flextable_aes(table_title = "Table 5. Goal attainment of low-density lipoprotein cholesterol, non-high-density lipoprotein cholesterol, and apolipoproteinB among US adults with a class I treatment indication per the 2026 ACC/AHA Dysylipidemia Guideline among those on pharmacotherapy, stratified by treatment goal.") %>%
  width(width = c(1.5, 1 %>% rep(3), 1.5, 1.5)) -> goal_need_3_t

#Save
  save_as_docx(goal_need_3_t, path = "Tables/Table 5.docx")

```


###Use of LLT

```{r}
sdata_ldl$variables[new_1 == "yes"][llt == "yes", sum(weight_ldl) %>% comma]
sdata_ldl$variables[new_1 == "yes"][llt == "yes" & statin == "yes", sum(weight_ldl)/sdata_ldl$variables[new_1 == "yes"][llt == "yes", sum(weight_ldl)]]
sdata_ldl$variables[new_1 == "yes"][llt == "yes" & ezetimibe == "yes", sum(weight_ldl)/sdata_ldl$variables[new_1 == "yes"][llt == "yes", sum(weight_ldl)]]
sdata_ldl$variables[new_1 == "yes"][llt == "yes" & pcsk9 == "yes", sum(weight_ldl)/sdata_ldl$variables[new_1 == "yes"][llt == "yes", sum(weight_ldl)]]


group_filters <- list(
  expr(ascvd == "yes"),
  expr(dm == "yes" & ascvd == "no"),
  expr(pre_ttt_ldl >= 190 & dm == "no" & ascvd == "no"),
  expr(dm == "no" & ascvd == "no" & pre_ttt_ldl < 190 & new_1 == "yes")
)
names(group_filters) <- c("ASCVD", "DM", "Pre-treatment LDL of 190 mg/dL or greater", "Primary prevention")

lapply(1:length(group_filters),
       function(i)
         data.table(
           group = names(group_filters)[i],
           n_total = sdata$variables[eval(group_filters[[i]]), sum(weight) %>% tomil],
           n_llt = sdata_ldl$variables[llt == "yes" & eval(group_filters[[i]]), sum(weight_ldl) %>% tomil],
           pct_llt = sdata_ldl$variables[eval(group_filters[[i]]),  sum(weight_ldl[llt == "yes"])/sdata$variables[eval(group_filters[[i]]), sum(weight)]]  %>% {r1(.*100)},
           median_ldl_overall = sdata_ldl$variables[eval(group_filters[[i]]), wtd_median_iqr(ldl, weight_ldl)],
           median_ldl_llt = sdata_ldl$variables[llt == "yes" & eval(group_filters[[i]]), wtd_median_iqr(ldl, weight_ldl)]
         )
       ) %>% rbindlist -> llt_use_df


flextable(llt_use_df[, .(`Group` = group,
                               `Number of adults, millions` = n_total,
                               `Number of adults on lipid-lowering therapy, millions` = n_llt,
                               `Proportion on lipid lowering therapy, %` = pct_llt,
                               `Overall median LDL-C (Interquartile range), mg/dL` = median_ldl_overall,
                         `On-treatment Median LDL-C (Interquartile range), mg/dL` = median_ldl_overall)]) %>%
  bold(j = c(1, 2)) %>%
  
  add_footer_row(values = as_paragraph("ASCVD: Atherosclerotic cardiovascular disease; DM: Diabetes mellitus; LDL-C: Low-density lipoprotein cholesterol"),
                 colwidths = 6) %>%
  add_footer_row(values = as_paragraph("Diabetes was defined by an HbA1c ≥6.5%, fasting glucose ≥126mg/dL, a self-reported history of diabetes, or use of medications specific to diabetes. ASCVD was defined by a self-reported history of myocardial infarction, coronary heart disease, angina, or stroke"),
                 colwidths = 6) %>%
  add_footer_row(values = as_paragraph(abbs_line),
                 colwidths = 6) %>%
  flextable_aes(table_title = "Supplementary Table 7. Utilization of lipid-lowering treatments and low-density lipoprotein cholesterol levels by treatment indication") %>%
  merge_v() %>%
  flextable::width(width = 1.2) -> llt_use_t
  save_as_docx(llt_use_t, path = "Tables/Supplementary Table 7.docx")

```

##E. Variables by discordance

### Overall

```{r}
get_svytotals(design = subset(sdata, llt == "no"),
              var = ~ discordant_type, n_cats = 4) -> discordant_df

```

###Functions

```{r}
#Experiment to make sure functions work correctly
# mean_var = ~ tc
# prop_var = ~ dm
# subset_var = "discordant_type"
# subset_options = discordant_type_options
# wanted_value = "yes"



#Means
mean_t_fn <- function(filtered_design = sdata %>%
                        subset(llt == "no"), 
                      mean_var, subset_var, subset_options) {
  #Get means and CIs
lapply(subset_options,
           function(i)
           svymean_df(design = filtered_design %>%
                        subset(get(subset_var) == i), mean_var)[, pe_ci]
           ) -> m

#Formulas to run regressions and compare
form1 <- formula(paste0(paste0(mean_var)[2], " ~ 1"))
form2 <- formula(paste0(paste0(mean_var)[2], " ~ discordant_type"))


#Compare
anova(
  svyglm(design = sdata %>% 
         subset(llt == "no") %>% 
         subset(discordant_type %>% str_detect("Discordant")),
       formula = form1
       ),
  svyglm(design = sdata %>% 
         subset(llt == "no") %>% 
         subset(discordant_type %>% str_detect("Discordant")),
       formula = form2
       ),
  method = "LRT"
)$p %>% p -> p_lrt

#String together
c(m,
  p_lrt
  )
  
}

#Test
# prop_var = ~ asian;
#       subset_var = "discordant_2_type";
#       subset_options = discordant_2_type_options;
#       wanted_value = "yes"
#       filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")

#Proprotions
prop_t_fn <- function(filtered_design = sdata %>%
                        subset(llt == "no"),
                      prop_var, subset_var, subset_options, wanted_value) {
  #Get proportions
lapply(subset_options,
         function(i)
           #If 0, don't run function
           if(filtered_design$variables[llt == "no" & get(subset_var) == i, .N, by = eval(paste0(prop_var)[2])] %>% na.omit %>% nrow == 1) 0 else {
           svytotal_df(design = filtered_design %>%
                         subset(get(subset_var) == i), prop_var)[value == wanted_value, prop_pe_ci]
           }
  ) -> m


#Formulas to run regressions and compare
form1 <- formula(paste0("factor(", paste0(prop_var)[2], ")", " ~ 1"))
form2 <- formula(paste0("factor(", paste0(prop_var)[2], ")", " ~ discordant_type"))

#Compare
anova(
  svyglm(design = sdata %>% 
         subset(llt == "no") %>% 
         subset(discordant_type %>% str_detect("Discordant")),
         family = "binomial",
       formula = form1
       ),
  svyglm(design = sdata %>% 
         subset(llt == "no") %>% 
         subset(discordant_type %>% str_detect("Discordant")),
         family = "binomial",
       formula = form2
       ),
  method = "LRT"
)$p %>% p -> p_lrt

#String together
c(m,
  p_lrt
  )
}

```

###Tabulate

#### Class I

```{r}

#discordant_type_options options
discordant_type_options <- data[, levels(discordant_type)]

#Produce list
list(
  #N
  c("Respondents in NHANES, N",
    sdata$variables[llt == "no", .N %>% comma, by = discordant_type][,V1], ""),
  c("US adults, N (millions)",
    sdata$variables[llt == "no", sum(weight) %>% tomil, by = discordant_type][,V1], ""),
  c("% of US Adults ≥20 years",
    svytotal_df(design = sdata %>%
                subset(llt == "no"), ~ discordant_type)$prop_pe_ci, ""),
  #Age
  c("Age (years)",
    mean_t_fn(mean_var = ~ age, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  #Sex
  c("Women (%)",
    prop_t_fn(prop_var = ~ sex,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "female")),
  #Race
  c("Race/ethnicity (%)", "", "", "", "", ""),
  c("     Non-Hispanic Black",
    prop_t_fn(prop_var = ~ black,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  c("     Hispanic",
    prop_t_fn(prop_var = ~ hispanic,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  c("     Non-Hispanic Asian",
    prop_t_fn(prop_var = ~ asian,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
    c("     Non-Hispanic White",
    prop_t_fn(prop_var = ~ white,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  c("     Other races and ethnicities (including multiracial)",
    prop_t_fn(prop_var = ~ other,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  #Parameters
    #Cholesterol
  c("Total cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ tc, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  c("HDL cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ hdl, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  c("Non-HDL cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ eval(tc - hdl), 
              subset_var = "discordant_type",
              subset_options = discordant_type_options)
  ),
  c("LDL cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ eval(ldl), 
              subset_var = "discordant_type",
              subset_options = discordant_type_options)
  ),
  #SBP
  c("Systolic blood pressure (mm Hg)",
    mean_t_fn(mean_var = ~ sbp, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  #DBP
  c("Diastolic blood pressure (mm Hg)",
    mean_t_fn(mean_var = ~ dbp, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  #BMI
  c("BMI (kg/m²)",
    mean_t_fn(mean_var = ~ bmi, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  #HbA1c
  c("HbA1c (%)",
    mean_t_fn(mean_var = ~ hba1c, 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  #Risk
  c("PCE 10-year ASCVD risk, %",
    mean_t_fn(mean_var = ~ eval(100*pce_10yr), 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  c("PREVENT 10-year ASCVD risk, %",
    mean_t_fn(mean_var = ~ eval(100*prevent_10yr), 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  c("PREVENT 30-year ASCVD risk, %",
    mean_t_fn(mean_var = ~ eval(100*prevent_30yr), 
              subset_var = "discordant_type", 
              subset_options = discordant_type_options)
  ),
  #CV RFs
  c("Cardiovascular risk factors (%)", " ", " ", " ", "", ""),
  c("     Obesity (%)",
    prop_t_fn(prop_var = ~ obesity,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  c("     CKD (%)",
    prop_t_fn(prop_var = ~ ckd,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  c("     Diabetes (%)",
    prop_t_fn(prop_var = ~ dm,
              subset_var = "discordant_type", 
              subset_options = discordant_type_options,
              wanted_value = "yes")),
  c("     ASCVD (%)",
    svytotal_df(sdata %>% subset(discordant_type == discordant_type_options[1]), ~ ascvd)[value == "yes", prop_pe_ci],
    svytotal_df(sdata %>% subset(discordant_type == discordant_type_options[2]), ~ ascvd)[value == "yes", prop_pe_ci],
    "N/A", "N/A", "N/A")
) -> disc_t_rfs_list
  




disc_t_rfs_list %>%
#Convert to a vector
  unlist %>%
  str_replace(" to  ", " to ") %>%
  #Morph into a table
  matrix(.,
         ncol = 6,
         byrow = T) %>%
  data.table -> disc_t_rfs_dt

lrt_line <- "Characteristics of individuals with discordant recommendations were compared using logistic regression, with the type of discordance (newly eligible vs newly ineligible) as the outcome variable. P values from likelihood ratio tests were obtained to determine statistical significance."


#Name columns
setnames(disc_t_rfs_dt,
         c("Variable", 
           "Eligible by both Guidelines",
           "Ineligible by both Guidelines",
           "Newly eligible",
           "No longer eligible",
           "P-value*"))

disc_t_rfs_dt %>%
  flextable %>%
  bold(j = c(1)) %>%
  add_footer_row(values = as_paragraph(lrt_line), colwidths = 6) %>%
  add_footer_row(values = as_paragraph("Values are presented as survey-weighted means (for continuous variables) and proportions (for categorical variables) with 95% confidence intervals."), colwidths = 6) %>%
    add_footer_row(values = as_paragraph(explanation_line), colwidths = 6) %>%
  add_footer_row(values = as_paragraph(paste0(abbs_line, "; PCE: Pooled Cohort Equations; PREVENT: Predicting Risk of Cardiovascular Disease Events." )), colwidths = 6) %>%
  flextable_aes(table_title = "Table 3. Characteristics of US adults according to the concordance or discordance of 2018 and 2026 ACC/AHA dyslipidemia Guidelines for the initiation of pharmacological treatment.") %>%
  add_header_row(values = c("", "Concordant", "Discordant"),
                 colwidths = c(1, 2, 3)
                 ) %>%
  
  align(align = "left") %>%
  fontsize(size = 10) %>%
  flextable::width(width = c(1.8, 1.3 %>% rep(4), 0.7)) %>%
    merge_h() -> disc_t_rfs_t
  save_as_docx(disc_t_rfs_t, path = "Tables/Table 3.docx")


```

#### Class I/II

```{r}

#discordant_12_type_options options
discordant_12_type_options <- data[, levels(discordant_12_type)]
setorder(sdata$variables, discordant_12_type)

#Produce list
list(
  #N
  c("Respondents in NHANES, N",
    sdata$variables[llt == "no", .N %>% comma, by = discordant_12_type][,V1], ""),
  c("US adults, N (millions)",
    sdata$variables[llt == "no", sum(weight) %>% tomil, by = discordant_12_type][,V1], ""),
  c("% of US Adults ≥20 years",
    svytotal_df(design = sdata %>%
                  subset(llt == "no"), ~ discordant_12_type)$prop_pe_ci, ""),
  #Age
  c("Age (years)",
    mean_t_fn(mean_var = ~ age, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  #Sex
  c("Women (%)",
    prop_t_fn(prop_var = ~ sex,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "female")),
  #Race
  c("Race/ethnicity (%)", "", "", "", "", ""),
  c("     Non-Hispanic Black",
    prop_t_fn(prop_var = ~ black,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     Hispanic",
    prop_t_fn(prop_var = ~ hispanic,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     Non-Hispanic Asian",
    prop_t_fn(prop_var = ~ asian,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     Non-Hispanic White",
    prop_t_fn(prop_var = ~ white,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     Other races and ethnicities (including multiracial)",
    prop_t_fn(prop_var = ~ other,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  #Parameters
  #Cholesterol
  c("Total cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ tc, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  c("HDL cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ hdl, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  c("Non-HDL cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ eval(tc - hdl), 
              subset_var = "discordant_12_type",
              subset_options = discordant_12_type_options)
  ),
  c("LDL cholesterol (mg/dL)",
    mean_t_fn(mean_var = ~ eval(ldl), 
              subset_var = "discordant_12_type",
              subset_options = discordant_12_type_options)
  ),
  #SBP
  c("Systolic blood pressure (mm Hg)",
    mean_t_fn(mean_var = ~ sbp, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  #DBP
  c("Diastolic blood pressure (mm Hg)",
    mean_t_fn(mean_var = ~ dbp, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  #BMI
  c("BMI (kg/m²)",
    mean_t_fn(mean_var = ~ bmi, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  #HbA1c
  c("HbA1c (%)",
    mean_t_fn(mean_var = ~ hba1c, 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  #Risk
  c("PCE 10-year ASCVD risk, %",
    mean_t_fn(mean_var = ~ eval(100*pce_10yr), 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  c("PREVENT 10-year ASCVD risk, %",
    mean_t_fn(mean_var = ~ eval(100*prevent_10yr), 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  c("PREVENT 30-year ASCVD risk, %",
    mean_t_fn(mean_var = ~ eval(100*prevent_30yr), 
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options)
  ),
  #CV RFs
  c("Cardiovascular risk factors (%)", " ", " ", " ", "", ""),
  c("     Obesity (%)",
    prop_t_fn(prop_var = ~ obesity,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     CKD (%)",
    prop_t_fn(prop_var = ~ ckd,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     Diabetes (%)",
    prop_t_fn(prop_var = ~ dm,
              subset_var = "discordant_12_type", 
              subset_options = discordant_12_type_options,
              wanted_value = "yes")),
  c("     ASCVD (%)",
    svytotal_df(sdata %>% subset(discordant_12_type == discordant_12_type_options[1]), ~ ascvd)[value == "yes", prop_pe_ci],
    svytotal_df(sdata %>% subset(discordant_12_type == discordant_12_type_options[2]), ~ ascvd)[value == "yes", prop_pe_ci],
    "N/A", "N/A", "N/A")
) -> disc_12_t_rfs_list


disc_12_t_rfs_list %>%
  #Convert to a vector
  unlist %>%
  str_replace(" to  ", " to ") %>%
  #Morph into a table
  matrix(.,
         ncol = 6,
         byrow = T) %>%
  data.table -> disc_12_t_rfs_dt

#Name columns
setnames(disc_12_t_rfs_dt,
         c("Variable", 
           "Eligible by both Guidelines",
           "Ineligible by both Guidelines",
           "Newly eligible",
           "No longer eligible",
           "P-value*"))

disc_12_t_rfs_dt %>%
  flextable %>%
  bold(j = c(1)) %>%
  add_footer_row(values = as_paragraph(lrt_line), colwidths = 6) %>%
  add_footer_row(values = as_paragraph("Values are presented as survey-weighted means (for continuous variables) and proportions (for categorical variables) with 95% confidence intervals."), colwidths = 6) %>%
    add_footer_row(values = as_paragraph("*Comparing  means/proportions in newly eligible vs newly ineligible persons"), colwidths = 6) %>%
  add_footer_row(values = as_paragraph("Values are presented as survey-weighted means (for continuous variables) and proportions (for categorical variables) with 95% confidence intervals."), colwidths = 6) %>%
    add_footer_row(values = as_paragraph(explanation_line), colwidths = 6) %>%
  add_footer_row(values = as_paragraph(paste0(abbs_line, "; PCE: Pooled Cohort Equations; PREVENT: Predicting Risk of Cardiovascular Disease Events." )), colwidths = 6) %>%
  flextable_aes(table_title = "Table 4. Characteristics of US adults according to the concordance or discordance of class I or II recommendations by the 2018 and 2026 ACC/AHA dyslipidemia Guidelines for the initiation of pharmacological treatment.") %>%
  align(align = "left") %>%
  fontsize(size = 10) %>%
  flextable::width(width = c(1.8, 1.3 %>% rep(4), 0.7)) %>%
  merge_h() -> disc_12_t_rfs
  save_as_docx(disc_12_t_rfs, path = "Tables/Table 4.docx")


```

#### II only

```{r}
#discordant_2_type_options options
discordant_2_type_options <- data[, levels(discordant_2_type)]

#Produce list
list(
  #N
  c("Respondents in NHANES, N",
    sdata$variables[llt == "no" & new_1 == "no" & old_1 == "no", .N %>% comma, by = discordant_2_type][,V1], ""),
  c("US adults, N (millions)",
    sdata$variables[llt == "no" & new_1 == "no" & old_1 == "no", sum(weight) %>% tomil, by = discordant_2_type][,V1], ""),
  c("% of US Adults ≥20 years",
    svytotal_df(design = sdata %>%
                  subset(llt == "no" & new_1 == "no" & old_1 == "no"), ~ discordant_2_type)$prop_pe_ci, ""),
  #Age
  c("Age (years)",
    mean_t_fn(
      mean_var = ~ age, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #Sex
  c("Women (%)",
    prop_t_fn(
      prop_var = ~ sex,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "female",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #Race
  c("Race/ethnicity (%)", "", "", "", "", ""),
  c("     Non-Hispanic Black",
    prop_t_fn(
      prop_var = ~ black,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     Hispanic",
    prop_t_fn(
      prop_var = ~ hispanic,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     Non-Hispanic Asian",
    prop_t_fn(
      prop_var = ~ asian,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     Non-Hispanic White",
    prop_t_fn(
      prop_var = ~ white,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     Other races and ethnicities (including multiracial)",
    prop_t_fn(
      prop_var = ~ other,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #Parameters
  #Cholesterol
  c("Total cholesterol (mg/dL)",
    mean_t_fn(
      mean_var = ~ tc, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("HDL cholesterol (mg/dL)",
    mean_t_fn(
      mean_var = ~ hdl, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("Non-HDL cholesterol (mg/dL)",
    mean_t_fn(
      mean_var = ~ eval(tc - hdl), 
      subset_var = "discordant_2_type",
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("LDL cholesterol (mg/dL)",
    mean_t_fn(
      mean_var = ~ eval(ldl), 
      subset_var = "discordant_2_type",
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #SBP
  c("Systolic blood pressure (mm Hg)",
    mean_t_fn(
      mean_var = ~ sbp, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #DBP
  c("Diastolic blood pressure (mm Hg)",
    mean_t_fn(
      mean_var = ~ dbp, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #BMI
  c("BMI (kg/m²)",
    mean_t_fn(
      mean_var = ~ bmi, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #HbA1c
  c("HbA1c (%)",
    mean_t_fn(
      mean_var = ~ hba1c, 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #Risk
  c("PCE 10-year ASCVD risk, %",
    mean_t_fn(
      mean_var = ~ eval(100*pce_10yr), 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("PREVENT 10-year ASCVD risk, %",
    mean_t_fn(
      mean_var = ~ eval(100*prevent_10yr), 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("PREVENT 30-year ASCVD risk, %",
    mean_t_fn(
      mean_var = ~ eval(100*prevent_30yr), 
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  #CV RFs
  c("Cardiovascular risk factors (%)", " ", " ", " ", "", ""),
  c("     Obesity (%)",
    prop_t_fn(
      prop_var = ~ obesity,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     CKD (%)",
    prop_t_fn(
      prop_var = ~ ckd,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     Diabetes (%)",
    prop_t_fn(
      prop_var = ~ dm,
      subset_var = "discordant_2_type", 
      subset_options = discordant_2_type_options,
      wanted_value = "yes",
      filtered_design = sdata %>% subset(llt == "no" & new_1 == "no" & old_1 == "no")
    )
  ),
  c("     ASCVD (%)",
    svytotal_df(
      sdata %>% subset(discordant_2_type == discordant_2_type_options[1] & new_1 == "no" & old_1 == "no"), 
      ~ ascvd
    )[value == "yes", prop_pe_ci],
    svytotal_df(
      sdata %>% subset(discordant_2_type == discordant_2_type_options[2] & new_1 == "no" & old_1 == "no"), 
      ~ ascvd
    )[value == "yes", prop_pe_ci],
    "N/A", "N/A", "N/A"
  )
) -> disc_2_t_rfs_list


disc_2_t_rfs_list %>%
  #Convert to a vector
  unlist %>%
  str_replace(" to  ", " to ") %>%
  #Morph into a table
  matrix(.,
         ncol = 6,
         byrow = T) %>%
  data.table -> disc_2_t_rfs_dt

#Name columns
setnames(disc_2_t_rfs_dt,
         c("Variable", 
           "Eligible by both Guideline",
           "Ineligible by both Guideline",
           "Newly eligible",
           "No longer eligible",
           "P-value*"))

disc_2_t_rfs_dt %>%
  flextable %>%
  bold(j = c(1)) %>%
  add_footer_row(values = as_paragraph(lrt_line), colwidths = 6) %>%
  add_footer_row(values = as_paragraph("Values are presented as survey-weighted means (for continuous variables) and proportions (for categorical variables) with 95% confidence intervals."), colwidths = 6) %>%
    add_footer_row(values = as_paragraph(explanation_line), colwidths = 6) %>%
  add_footer_row(values = as_paragraph(paste0(abbs_line, "; PCE: Pooled Cohort Equations; PREVENT: Predicting Risk of Cardiovascular Disease Events." )), colwidths = 6) %>%
  flextable_aes(table_title = "Supplementary Table XXX [Redundant]. Characteristics of US adults according to the concordance or discordance of class II recommendations by the 2018 and 2026 ACC/AHA dyslipidemia Guidelines for the initiation of pharmacological treatment.") %>%
  align(align = "left") %>%
  fontsize(size = 10) %>%
  flextable::width(width = c(1.8, 1.3 %>% rep(4), 0.7)) %>%
  merge_h() -> disc_2_t_rfs

  save_as_docx(disc_2_t_rfs, path = "Tables/Supplementary Table XXX [Redundant].docx")


```

##Produce Tables
```{r}


# Put all your tables in a list in the order you want them
all_tables <- list(
  t1_t_list[[1]],
  t1_t_list[[2]],
  disc_t_rfs_t,
  disc_12_t_rfs,
  goal_need_3_t,
  missing_data_t,
  baseline_table_t,
  t1_t_list[[6]],
  llt_use_t
)
library(officer)
# Initialize Word document
all_tables_doc <- read_docx()

# Loop through tables and add them with a break after each
for(tbl in all_tables) {
  all_tables_doc <- all_tables_doc %>%
    body_add_flextable(tbl) %>%
    body_add_break(pos = "after")
}
print(all_tables_doc, target = "Tables/Compiled Tables.docx")


```

# Save

```{r}
inclusion <- expr(age >= 20 & !is.na(new_1) & !is.na(old_1))
save(
  #Datasets
  data, sdata,
  #Datapoints
  old_1_df, new_1_df, 
  disc_t_rfs_dt, goal_need_cat_df,
  abs_diff_init_df,
   discordant_df, age_df, age_sex_df,
  inclusion, long_short_df, cacs_df,
  mid_aged_prop_df,
  hiv_df, hiv_sex_df, hiv_old_df,
  ratio_qs, new_2a_ldl30_df_prop,
   #Main Figures
  fig1, fig2, fig3, fig4, fig5,
  #Figure belonings
  females_ypos, females_label,
  males_label, males_ypos,
   #File
   file = "Rendering Data.RData")

```
